---
title: "Usage of Prophylactic Dexamethasone to Reduce Incidence and Severity of Toxicity after Ciltacabtagene autoleucel"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: kable
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library, echo = FALSE}
library(tidyverse)
library(labelled)
library(gtsummary)
library(survminer)
library(survival)
theme_gtsummary_compact()
theme_set(theme_classic())
```


```{r load}
# The repository is saved here 
# Peres_Research/Myeloma/Analyses/Prophylactic Dexamethasone/Rproject/toxocity_prophylactic_dexamethasone
path <- fs::path("","Volumes","Peres_Research", "")

clinical <-
  readxl::read_xlsx(paste0(#path, 
                           here::here(), "/data/raw_data",
                           "/Carvykti Data Collection Sheet 2.2.26.xlsx"), 
                    na = c("NR", "NA", "Na"),
                    skip = 1) %>% 
  janitor::clean_names()

consortium <-
  readxl::read_xlsx(paste0(#path, 
                           here::here(), "/data/raw_data",
                           "/dougas_prophy_dex_data_01-27-2026.xlsx"), 
                    na = c("unk", "na")
                    ) %>% 
  janitor::clean_names()
gabe_data <-
  readxl::read_xlsx(paste0(#path, 
                           here::here(), "/data/raw_data",
                           "/dougas_prophy_dex_vitalstatus_response_data_02-18-2026.xlsx"), 
                    na = c("unk")
                    ) %>% 
  janitor::clean_names()
```

```{r exploratory function}
data <- clinical %>%
  # select_if(~!is.numeric(.)) %>%
  select_if(~!is.POSIXct(.))
data <- consortium %>%
  # select_if(~!is.numeric(.)) %>%
  select_if(~!is.POSIXct(.))

# check_data <- function(data){
# 
#   for(i in 1:length(colnames(data))) {
# 
#     # if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
# 
#       # print(data[i])
#       print(colnames(data[i]))
#       print(str(data[[i]]))
#       print(table(data[[i]]))
#     # }
# 
#   }
# }
# 
# check_data(data[2:50])
# check_data(data[51:100])
# check_data(data[101:150])
# check_data(data[151:187])

# check_data(data[2:28])
```

```{r consortium cleaning}
consortium1 <- consortium %>% 
  select(-c(outcomes_resp_d30, outcomes_resp_d90, 
            outcomes_resp_d180, outcomes_resp_d360, 
            outcomes_prog_dt, mortality,
            mortality_dt, mortality_cause)) %>% 
  left_join(., gabe_data,
            by = c("key_mrn", "key_ptid")) %>% 
  mutate(cartchar_infusion_dose = case_when(
    cartchar_infusion_dose == 999999                   ~ 0.6,
    TRUE                                               ~ cartchar_infusion_dose
  )) %>% 
  mutate(r_iss = na_if(r_iss, "Unable to Calculate")) %>% 
  `colnames<-`(paste0("updated_", colnames(.)))
```

```{r verification function}
data <- consortium1 %>%
  # select_if(~!is.numeric(.)) %>%
  select_if(~!is.POSIXct(.))

# check_data <- function(data){
# 
#   for(i in 1:length(colnames(data))) {
# 
#     # if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
# 
#       # print(data[i])
#       print(colnames(data[i]))
#       print(str(data[[i]]))
#       print(table(data[[i]]))
#     # }
# 
#   }
# }

# check_data(data[2:28])
```

```{r merge}
clinical <- clinical %>% 
  # General ----
  # Fix letter case and missing
  mutate(across(c(where(is.character),
                  - c("nint_type",
                      "d_30", "d_90", "d_180", "d_365")),# c("tumor_bcma_expression"),
                ~ str_to_sentence(.) )) %>%
  # mutate(across(c(contains("vgpr"), "response_to_bridging_chemotherapy"
  #                 ),
  #               ~ str_to_upper(.) )) %>%
  mutate(across(where(is.character),
                ~ str_replace(., "^Unknown$", NA_character_))) %>%
  # Merge----
  inner_join(., consortium1, by = c("mrn" = "updated_key_mrn"))
```

```{r clinical cleaning}
cart <- clinical %>%
  # Demo----
  mutate(agecat = case_when(
    age_d0 < 70                                         ~ "< 70 years",
    age_d0 >= 70                                        ~ "≥ 70 years"
  ),
  agecat = factor(agecat, levels = c("< 70 years", "≥ 70 years"))
  ) %>%
  mutate(race = case_when(
    race == "W"                        ~ "White",
    race == "B"                        ~ "Black",
    race == "Api"                      ~ "Asian/Pacific Islander",
    race == "O"                        ~ "Other",
    TRUE                               ~ race
  )) %>%
  # Yes/No----
  mutate_at(c("ppx_dex_cohort_y_n",
              "ecog_performance_status_0_1_y_n",
              "hx_of_previous_malignancy_y_n",
              "extramedullary_disease_y_n",
              "past_exposure_to_bcma_y_n",
              "prior_cart_exposure",
              "bm_bx_pre_bridging_60_percent_plasma_cells",
              "bridging_therapy_y_n",
              "ivig_given_y_n",
              "hospital_admit_y_n",
              "crs_y_n",
              "crs_tx_dex_y_n",
              "crs_toci_given",
              "crs_anakinra_given",
              "crs_anakinra_given",
              "icans_y_n",
              "icans_tx_dex_y_n",
              "icans_anakinra_given",
              "icans_other_therapies",
              "nint_y_n",
              "nint_tx_dex_y_n",
              "nint_ivig_given",
              "nint_other_therapies",
              "ivig_ppx",
              "infectious_complications_90_day",
              "severe_infection",
              "other_g3_4_toxicities_y_n",
              "mortality",
              "d_30_non_relapse_mortality"),
            ~ case_when(
              . == "Y"                 ~ "Yes",
              . == "N"                 ~ "No",
              TRUE                     ~ .
            )) %>%
  # Sex categories----
  mutate(sex_m_f = case_when(
    sex_m_f == "M"                     ~ "Male",
    sex_m_f == "F"                     ~ "Female"
  )) %>%
  mutate(male_sex = case_when(
    sex_m_f == "Male"                  ~ 1,
    sex_m_f == "Female"                ~ 0
  )) %>%

  # ECOG
  mutate(ecog_cat = case_when(
    ecog_performance_status == 0 |
      ecog_performance_status == 1     ~ "0-1",
    ecog_performance_status %in% c(2:4)  ~ "2-4"
  )) %>%

  # Disease ----
  mutate(r_iss_staging_2 = case_when(
    r_iss_staging_2 == 1               ~ "I",
    r_iss_staging_2 == 2               ~ "II",
    r_iss_staging_2 == 3               ~ "III",
    TRUE                               ~ r_iss_staging_2
  )) %>%
  mutate(car_hematotox_score_aph_cat = case_when(
    car_hematotox_score_aph %in%
      c(0:3)                           ~ "0-3",
    car_hematotox_score_aph > 3        ~ "4+"
  )) %>%
  mutate(car_hematotox_score_clear_cat = case_when(
    car_hematotox_score_clear %in%
      c(0:3)                           ~ "0-3",
    car_hematotox_score_clear > 3      ~ "4+"
  )) %>%
  mutate(peak_alc_grouping = case_when(
    peak_alc_grouping == 0             ~ "ALC ≥ 3",
    peak_alc_grouping == 1             ~ "ALC < 3",
  )) %>%
  mutate(peak_alc_grouping_recoded = case_when(
    peak_alc >= 3                      ~ "ALC ≥ 3",
    peak_alc < 3                       ~ "ALC < 3",
  )) %>% 
  mutate(alc_treated = case_when(
    alc_treated == 0                   ~ "Not treated",
    alc_treated == 1                   ~ "Dexamethasone",
    alc_treated == 2                   ~ "Dexamethasone + Cyclophosphamide"
  ))
```

```{r infusion}
cart <- cart %>%
  mutate(notinfused = case_when(
    !is.na(date_of_carvykti_d0)        ~ "Yes",
    TRUE                               ~ "No"
  ))
```


```{r treatment}
cart <- cart %>%
  mutate(prior_transplant = case_when(
    prior_transplant == "N"            ~ "No",
    TRUE                               ~ prior_transplant
  )) %>%
  mutate(prior_auto_sct_y_n = case_when(
    prior_transplant == "No"           ~ "No",
    prior_transplant == "Auto"         ~ "Yes",
    prior_transplant == "Allo"         ~ "No"
  )) %>%
  mutate(prior_allo_sct_y_n = case_when(
    prior_transplant == "No"           ~ "No",
    prior_transplant == "Auto"         ~ "No",
    prior_transplant == "Allo"         ~ "Yes"
  )) %>%
  mutate(number_prior_lines_therapy = case_when(
    number_of_prior_therapies %in% c(1:3)                 ~ "1-3",
    number_of_prior_therapies > 3                         ~ "4 or more"
  )) %>%
  mutate(bridging_type = case_when(
    bridging_grouping == 0             ~ "Conventional chemoimmunotherapy",
    bridging_grouping == 1             ~ "GPRC5D-based regimen",
  )) %>% 
  mutate(crs_emapalumab_given = case_when(
    crs_other_therapies == "Emapalumab"                ~ "Yes",
    crs_y_n == "Yes"                                   ~ "No"
  )) %>% 
  mutate(crs_or_icans_dex_given_y_n = case_when(
    crs_tx_dex_y_n == "Yes"                            ~ "Yes",
    icans_tx_dex_y_n == "Yes"                          ~ "Yes",
    crs_tx_dex_y_n == "No" &
      icans_tx_dex_y_n == "No"                         ~ "No"
  )) %>% 
  mutate(crs_and_icans_dex_given_y_n = case_when(
    crs_tx_dex_y_n == "Yes" &
      icans_tx_dex_y_n == "Yes"                        ~ "Yes",
    crs_tx_dex_y_n == "No" &
      icans_tx_dex_y_n == "No"                         ~ "No"
  )) %>% 
  mutate(nint_tx_dex_y_n = case_when(
    nint_tx_dex_y_n == "Yes"                           ~ "Yes",
    is.na(nint_tx_dex_y_n) &
      nint_y_n == "Yes"                                ~ "No"
  ))


  # date_of_carvykti_d0 # has a weird date format but seems ok
  # time_from_bridging_to_car_t
  # carvykti_cell_dose
  # crs_days_of_tx_dex
  # crs_tx_dex_given
  # crs_other_therapies
  # icans_days_of_tx_dex
  # icans_tx_dex_given
  # all crs and icans

```

```{r toxicities}
cart2 <- cart %>%
# CRS ----
  mutate(CRS_any = ifelse(crs_highest_grade == 0, "No", "Yes"),
       CRS_any2 = ifelse(CRS_any == "No", 0, 1),
       CRS_gradecat2 = case_when(
         crs_highest_grade == 0                        ~ "No CRS",
         crs_highest_grade == 1                        ~ "Grade 1",
         crs_highest_grade >= 2                        ~ "Grade 2+"),
       CRS_gradecat2 = factor(CRS_gradecat2, levels = c("No CRS", "Grade 1", "Grade 2+")),
       CRS_gradecat3 = case_when(
         crs_highest_grade == 0                        ~ "No CRS",
         crs_highest_grade %in% c(1:2)                 ~ "Grade 1 or 2",
         crs_highest_grade >= 3                        ~ "Grade 3+"),
       CRS_gradecat3 = factor(CRS_gradecat3, levels = c("No CRS", "Grade 1 or 2", "Grade 3+"))
  ) %>% 
  mutate(gr3_CRS = case_when(
    crs_highest_grade %in% c(1:2)                      ~ "Grade <3",
    crs_highest_grade %in% c(3:5)                      ~ "Grade ≥3"
  )) %>%
  mutate(gr2_CRS = case_when(
    crs_highest_grade %in% c(1)                        ~ "Grade <2",
    crs_highest_grade %in% c(2:5)                      ~ "Grade ≥2"
  )) %>%
  mutate(day_of_onset_crs_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = crs_day_of_onset) /
           duration(n =1, unit = "days")
  ) %>%
  # mutate(day_of_max_crs_relative_to_infusion =
  #          interval(start = date_of_carvykti_d0, end = date_of_max_crs) /
  #          duration(n =1, unit = "days")
  # ) %>%

  # ICANS ----
  mutate(ICANS_any = ifelse(icans_highest_grade == 0, "No", "Yes"),
       ICANS_any2 = ifelse(ICANS_any == "No", 0, 1),
       ICANS_gradecat2 = case_when(
         icans_highest_grade == 0                      ~ "No ICANS",
         icans_highest_grade == 1                      ~ "Grade 1",
         icans_highest_grade >= 2                      ~ "Grade 2+"),
       ICANS_gradecat2 = factor(ICANS_gradecat2, levels = c("No CRS", "Grade 1", "Grade 2+")),
       ICANS_gradecat3 = case_when(
         icans_highest_grade == 0                      ~ "No ICANS",
         icans_highest_grade %in% c(1:2)               ~ "Grade 1 or 2",
         icans_highest_grade >= 3                      ~ "Grade 3+"),
       ICANS_gradecat3 = factor(ICANS_gradecat3, levels = c("No CRS", "Grade 1 or 2", "Grade 3+")),
       gr3_ICANS = case_when(
         icans_highest_grade %in% c(1:2)               ~ "Grade <3",
         icans_highest_grade %in% c(3:5)               ~ "Grade ≥3"
       )) %>%
  mutate(gr2_ICANS = case_when(
    icans_highest_grade %in% c(1)                      ~ "Grade <2",
    icans_highest_grade %in% c(2:5)                    ~ "Grade ≥2"
  )) %>%
  mutate(day_of_onset_icans_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = icans_day_of_onset) /
           duration(n =1, unit = "days")
  ) %>%
  # NINT----
  # mutate(parkinsonian_neurotoxicity_yes_no = case_when(
  #   nint_y_n == "No"                                   ~ "No",
  #   str_detect(nint_type, "Parkinsonism")              ~ "Yes",
  #   !is.na(nint_type)                                  ~ "No",
  #   nint_y_n == "Yes"                                  ~ "Unk"
  # )) %>%
  mutate(parkinsonian_neurotoxicity_duration_days =
           interval(start = updated_dnt_parkinsononset_dt, end = updated_dnt_parkinsonlatest_dt) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(day_of_onset_parkinsonian_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = updated_dnt_parkinsononset_dt) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(cnp_duration_days =
           interval(start = updated_dnt_cnponset_dt, end = updated_dnt_cnplatest_dt) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(day_of_onset_cnp_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = updated_dnt_cnponset_dt) /
           duration(n =1, unit = "days")
  ) %>%
  
  mutate(day_of_onset_nint_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = nint_day_of_onset) /
           duration(n =1, unit = "days")
  ) %>%
  # mutate(day_of_icans_highest_grade_relative_to_infusion =
  #          interval(start = date_of_carvykti_d0, end = date_of_icans_highest_grade) /
  #          duration(n =1, unit = "days")
  # ) %>%
  mutate(clearance_ferritin = case_when(
    ferritin_clear < 650                               ~ "< 650",
    ferritin_clear %in% c(650:2000)                    ~ "650 - 2000",
    ferritin_clear > 2000                              ~ "> 2000"
  )) %>% 
  mutate(any_infection = infectious_complications_90_day) %>%
  mutate(any_sevinfection = case_when(
    !is.na(severe_infection)                           ~ severe_infection,
    any_infection == "No"                              ~ "No"
  )) %>%
  mutate(severe_infection = case_when(
    severe_infection == "Yes"                          ~ "Severe infection",
    severe_infection == "No"                           ~ "Mild-to-Moderate infection"
  )) %>%
  mutate(severity_infection = case_when(
    !is.na(severe_infection)                           ~ severe_infection,
    any_infection == "Yes"                             ~ "Yes",
    any_infection == "No"                              ~ "No infection"
  ), severity_infection = relevel(factor(severity_infection), ref = "No infection")) %>%
  mutate(time_from_infusion_to_infection_days =
           interval(start = date_of_carvykti_d0, end = date_of_severe_infection) /
           duration(n =1, unit = "days")
  )
```



```{r survival and response}
cart3 <- cart2 %>%
  # os
  mutate(updated_mortality = case_when(
    updated_mortality == "Y"                        ~ "Yes",
    updated_mortality == "N"                        ~ "No"
  )) %>% 
  # Fix event accordingly
  mutate(os_event = case_when(
    !is.na(updated_mortality_dt)                    ~ 1,
    is.na(updated_mortality_dt)                     ~ 0
  )) %>%
  mutate(os_date = coalesce(updated_vitalstatus_dt, date_of_last_visit_contact)) %>%
  mutate(os_from_infusion_months =
           interval(
             start = date_of_carvykti_d0,
             end = os_date)/
           duration(n = 1, units = "months")) %>%
  mutate(updated_day_of_death_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = updated_mortality_dt) /
           duration(n = 1, unit = "days")
  ) %>% 
  mutate(pfs_event = case_when(
    !is.na(updated_outcomes_prog_dt)                ~ 1,
    os_event == 1                                   ~ 1,
    !is.na(updated_vitalstatus_dt)                  ~ 0
  )) %>% 
  mutate(pfs_date = case_when(
    !is.na(updated_outcomes_prog_dt)                ~ updated_outcomes_prog_dt,
    os_event == 1                                   ~ os_date,
    !is.na(date_of_last_visit_contact)              ~ os_date
  )) %>% 
  mutate(pfs_from_infusion_months =
           interval(
             start = date_of_carvykti_d0,
             end = pfs_date)/
           duration(n = 1, units = "months")) %>%
  mutate(updated_day_of_prog_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = updated_outcomes_prog_dt) /
           duration(n = 1, unit = "days")
  )

cart3 <- cart3 %>% 
  mutate(response_d30 = case_when(
    str_detect(updated_outcomes_resp_d30, "VGPR")      ~ "VGPR",
    str_detect(updated_outcomes_resp_d30, "PR")        ~ "PR",
    str_detect(updated_outcomes_resp_d30, "uCR")	     ~ "sCR/CR",
    str_detect(updated_outcomes_resp_d30, "CR")        ~ "sCR/CR",
    updated_outcomes_resp_d30 == "MR"                  ~ "SD",
    str_detect(updated_outcomes_resp_d30, "SD")        ~ "SD",
    str_detect(updated_outcomes_resp_d30, "PD")        ~ "PD",
    (os_event == 1 | pfs_event == 1) & 
      pfs_from_infusion_months < 1                     ~ "Died or progressed before day 30",
    is.na(updated_outcomes_resp_d30)                   ~ NA_character_,
    TRUE                                               ~ updated_outcomes_resp_d30
  )) %>%
  mutate(response_d30_v2 = case_when(
    str_detect(response_d30, "Died")                   ~ "PD",
    is.na(response_d30)                                ~ NA_character_,
    TRUE                                               ~ response_d30
  )) %>% 
  mutate(ORR_30days = case_when(
    str_detect(response_d30_v2, "CR|PR")               ~ "≥PR",
    is.na(response_d30_v2)                             ~ NA_character_,
    TRUE                                               ~ "PD/SD" # = "PD/SD/MR"
  )) %>%
  # mutate(VGPRorbetter_30days = case_when(
  #   str_detect(response_d30, "CR|VGPR")                       ~ "VGPR/CR/sCR",
  #   is.na(response_d30)                                       ~ NA_character_,
  #   TRUE                                                      ~ "PD/SD"
  # )) %>%
  mutate(CRorbetter_30days = case_when(
    str_detect(response_d30_v2, "CR")	                 ~ "sCR/CR",
    is.na(response_d30_v2)                             ~ NA_character_,
    TRUE                                               ~ "≤CR"
  )) %>% 
  # mutate(CRorbetter_30days = case_when(
  #   response_d30 == "PD"	                                    ~ "Yes, PD",
  #   is.na(response_d30)                                       ~ NA_character_,
  #   TRUE                                                      ~ "No"
  # )) %>% 
  
  mutate(response_d90 = case_when(
    str_detect(updated_outcomes_resp_d90, "VGPR")      ~ "VGPR",
    str_detect(updated_outcomes_resp_d90, "PR")        ~ "PR",
    str_detect(updated_outcomes_resp_d90, "uCR")	     ~ "sCR/CR",
    str_detect(updated_outcomes_resp_d90, "CR")        ~ "sCR/CR",
    updated_outcomes_resp_d90 == "MR"                  ~ "SD",
    str_detect(updated_outcomes_resp_d90, "SD")        ~ "SD",
    str_detect(updated_outcomes_resp_d90, "PD")        ~ "PD",
    (os_event == 1 | pfs_event == 1) & 
      pfs_from_infusion_months < 3                     ~ "Died or progressed before day 90",
    is.na(updated_outcomes_resp_d90)                   ~ NA_character_,
    TRUE                                               ~ updated_outcomes_resp_d90
  )) %>%
    mutate(response_d90_v2 = case_when(
    str_detect(response_d90, "Died")                   ~ "PD",
    is.na(response_d90)                                ~ NA_character_,
    TRUE                                               ~ response_d90
  )) %>% 
  mutate(ORR_90days = case_when(
    str_detect(response_d90_v2, "CR|PR")               ~ "≥PR",
    is.na(response_d90_v2)                             ~ NA_character_,
    TRUE                                               ~ "PD/SD"
  )) %>%
  mutate(CRorbetter_90days = case_when(
    str_detect(response_d90_v2, "CR")	                 ~ "sCR/CR",
    is.na(response_d90_v2)                             ~ NA_character_,
    TRUE                                               ~ "≤CR"
  )) %>%
  mutate(best_response_in90days = case_when(
    response_d30_v2 == "sCR/CR" | 
      response_d90_v2 == "sCR/CR"                      ~ "sCR/CR",
    response_d30_v2 == "VGPR" | 
      response_d90_v2 == "VGPR"                        ~ "VGPR",
    response_d30_v2 == "PR" | 
      response_d90_v2 == "PR"                          ~ "PR",
    response_d30_v2 == "SD" | 
      response_d90_v2 == "SD"                          ~ "SD",
    response_d30_v2 == "PD" | 
      response_d90_v2 == "PD"                          ~ "PD",
    TRUE                                               ~ NA_character_
  )) %>% 
  mutate(response_d180 = case_when(
    str_detect(updated_outcomes_resp_d180, "VGPR")     ~ "VGPR",
    str_detect(updated_outcomes_resp_d180, "PR")       ~ "PR",
    str_detect(updated_outcomes_resp_d180, "uCR")	     ~ "sCR/CR",
    str_detect(updated_outcomes_resp_d180, "CR")       ~ "sCR/CR",
    updated_outcomes_resp_d180 == "MR"                 ~ "SD",
    str_detect(updated_outcomes_resp_d180, "SD")       ~ "SD",
    str_detect(updated_outcomes_resp_d180, "PD")       ~ "PD",
    (os_event == 1 | pfs_event == 1) & 
      pfs_from_infusion_months < 6                     ~ "Died or progressed before day 180",
    is.na(updated_outcomes_resp_d180)                  ~ NA_character_,
    TRUE                                               ~ updated_outcomes_resp_d180
  )) %>%
    mutate(response_d180_v2 = case_when(
    str_detect(response_d180, "Died")                  ~ "PD",
    is.na(response_d180)                               ~ NA_character_,
    TRUE                                               ~ response_d180
  )) %>% 
  mutate(ORR_180days = case_when(
    str_detect(response_d180_v2, "CR|PR")              ~ "≥PR",
    is.na(response_d180_v2)                            ~ NA_character_,
    TRUE                                               ~ "PD/SD"
  )) %>%
  mutate(CRorbetter_180days = case_when(
    str_detect(response_d180_v2, "CR")	               ~ "sCR/CR",
    is.na(response_d180_v2)                            ~ NA_character_,
    TRUE                                               ~ "≤CR"
  )) %>%
  mutate(response_d360 = case_when(
    str_detect(updated_outcomes_resp_d360, "VGPR")     ~ "VGPR",
    str_detect(updated_outcomes_resp_d360, "PR")       ~ "PR",
    str_detect(updated_outcomes_resp_d360, "uCR")	     ~ "sCR/CR",
    str_detect(updated_outcomes_resp_d360, "CR")       ~ "sCR/CR",
    updated_outcomes_resp_d360 == "MR"                 ~ "SD",
    str_detect(updated_outcomes_resp_d360, "SD")       ~ "SD",
    str_detect(updated_outcomes_resp_d360, "PD")       ~ "PD",
    (os_event == 1 | pfs_event == 1) & 
      pfs_from_infusion_months < 12                    ~ "Died or progressed before day 360",
    is.na(updated_outcomes_resp_d360)                  ~ NA_character_,
    TRUE                                               ~ updated_outcomes_resp_d360
  )) %>%
    mutate(response_d360_v2 = case_when(
    str_detect(response_d360, "Died")                  ~ "PD",
    is.na(response_d360)                               ~ NA_character_,
    TRUE                                               ~ response_d360
  )) %>% 
  mutate(ORR_360days = case_when(
    str_detect(response_d360_v2, "CR|PR")              ~ "≥PR",
    is.na(response_d360_v2)                            ~ NA_character_,
    TRUE                                               ~ "PD/SD"
  )) %>%
  mutate(CRorbetter_360days = case_when(
    str_detect(response_d360_v2, "CR")	               ~ "sCR/CR",
    is.na(response_d360_v2)                            ~ NA_character_,
    TRUE                                               ~ "≤CR"
  )) %>%
  mutate(best_response = case_when(
    response_d30_v2 == "sCR/CR" | 
      response_d90_v2 == "sCR/CR" |
      response_d180_v2 == "sCR/CR" |
      response_d360_v2 == "sCR/CR"                     ~ "sCR/CR",
    response_d30_v2 == "VGPR" | 
      response_d90_v2 == "VGPR" | 
      response_d180_v2 == "VGPR" | 
      response_d360_v2 == "VGPR"                       ~ "VGPR",
    response_d30_v2 == "PR" | 
      response_d90_v2 == "PR" | 
      response_d180_v2 == "PR" | 
      response_d360_v2 == "PR"                         ~ "PR",
    response_d30_v2 == "SD" | 
      response_d90_v2 == "SD" | 
      response_d180_v2 == "SD" | 
      response_d360_v2 == "SD"                         ~ "SD",
    response_d30_v2 == "PD" | 
      response_d90_v2 == "PD" | 
      response_d180_v2 == "PD" | 
      response_d360_v2 == "PD"                         ~ "PD",
    TRUE                                               ~ NA_character_
  )) %>% 
  mutate(best_ORR = case_when(
    str_detect(best_response, "CR|PR")                 ~ "≥PR", 
    str_detect(best_response, "SD|PD")                 ~ "PD/SD",
    TRUE                                               ~ NA_character_
  )) %>% 
  mutate(best_CRorbetter = case_when(
     CRorbetter_30days == "sCR/CR" | 
       CRorbetter_90days == "sCR/CR" | 
       CRorbetter_180days == "sCR/CR" | 
       CRorbetter_360days == "sCR/CR"                  ~ "sCR/CR",
     is.na(CRorbetter_30days) & 
       is.na(CRorbetter_90days) & 
       is.na(CRorbetter_180days) & 
       is.na(CRorbetter_360days)                       ~ NA_character_, 
     TRUE                                              ~ "< CR"
   ))

```

```{r exploratory function2}
data <- cart3 %>%
  select_if(~!is.numeric(.)) %>%
  select_if(~!is.POSIXct(.))

# check_data <- function(data){
#
#   for(i in 1:length(colnames(data))) {
#
#     # if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
#
#       # print(data[i])
#       print(colnames(data[i]))
#       print(str(data[[i]]))
#       print(table(data[[i]]))
#     # }
#
#   }
# }
#
# check_data(data)
```

<!-- Issues for nint_d : 1 missing value. I calculated it myself (result in day_of_onset_nint_relative_to_infusion) -->
```{r}
# cart3 %>% 
#   filter(nint_y_n == "Yes") %>% 
#   select(mrn, nint_y_n, nint_d,
#          day_of_onset_nint_relative_to_infusion, nint_day_of_onset)

nint_dat <- cart3 %>% 
  select(mrn, starts_with("updated_dnt"), nint_y_n : nint_other_therapies, day_of_onset_nint_relative_to_infusion)
```

```{r Labeling}
## Labeling ----
var_label(cart3) <- list(age_d0 = "Patient age", agecat = "Patient age - Categories",
                         male_sex = "Male Sex", sex_m_f = "Sex",
                         race = "Race",
                         # raceeth = "Race and ethnicity",
                         notinfused = "Infused?",
                         os_from_infusion_months = "Follow-up time from infusion (months)",
                         
                         # mortality = "Death",
                         # day_of_death_relative_to_infusion = "Time-to-death (days)",
                         updated_day_of_death_relative_to_infusion = "Time-to-death (days)",
                         updated_mortality = "Death",
                         # day_of_prog_relative_to_infusion = "Time-to-progression (days)",
                         updated_day_of_prog_relative_to_infusion = "Time-to-progression (days)",
                         
                         
                         time_since_diagnosis_to_d0_years = "Time since diagnosis at D0 (years)",
                         # extramedullary_disease_y_n = "Extramedullary disease",
                         updated_bximag_imaging_emd_yn_preinf = "Extramedullary disease",
                         # circulating_plasma_cell = "UPDATED Circulating Plasma Cells",
                         # high_marrow_burden_50_percent = "High marrow burden (≥50%)",
                         ecog_performance_status = "ECOG",
                         ecog_cat = "ECOG (cat)" ,
                         r_iss_staging_2 = "R-ISS",
                         updated_r_iss = "R-ISS (Gabe)",
                         cytogenetic_risk = "High risk cytogenetics",
                         # cytogenetics_incl_1q = "High risk cytogenetics (including gain 1q)",
                         # deletion_17p_prior_to_car_t_infusion_y_n = "Deletion 17p at Infusion",
                         # t_4_14_prior_to_car_t_infusion_y_n = "t(4:14) at Infusion",
                         # t_14_16_prior_to_car_t_infusion_y_n = "t(4:16) at Infusion",
                         # gain_amp1q21 = "Gain/amp 1q21",
                         number_of_prior_therapies = "Number of prior therapy",
                         number_prior_lines_therapy = "Number of prior lines of therapy (cat)",
                         bm_bx_pre_bridging_60_percent_plasma_cells = "BMBx Pre Bridging ≥60% plasma cells",
                         prior_transplant =	"Previous stem-cell transplantation",
                         scope_mm = "SCOPE-MM",
                         bridging_therapy_y_n = "Bridging Therapy",
                         bridging_type = "Bridging therapy used",
                         prior_auto_sct_y_n = "Prior autoSCT",
                         prior_allo_sct_y_n = "Prior alloSCT",
                         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_y_n = "Prior BCMA-directed therapy",
                         past_exposure_to_bcma_y_n = "Prior BCMA-directed therapy",
                         # need_for_g_csf_post_infus_yes_1_no_0 = "Granulocyte colony stimulating factor (G-CSF)",
                         ivig_given_y_n = "Intravenous immunoglobulin (IVIG) prior to D0",
                         # cd34_stem_cell_boost_yes_1_no_0 = "CD34 stem cell boost",
                         # day_of_neutrophil_recovery = "Day of neutrophil recovery",
                         # transfusion_postCART = "Transfusion post-CAR T",
                         # tpo_agonist_post_cart_yes_1_no_0 = "Thrombopoietin (TPO) agonist",
                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese",
                         # steroid_use_y_n = "Steroid Use",
                         crs_toci_given = "Tocilizumab Use (CRS)",
                         crs_anakinra_given = "Anakinra Use (CRS)",
                         crs_emapalumab_given = "Emapalumab Use (CRS)",
                         crs_tx_dex_y_n = "Dexamethasone Use (CRS) - column CQ",
                         icans_anakinra_given = "Anakinra Use (ICANS)",
                         icans_tx_dex_y_n = "Dexamethasone Use (ICANS) - column DE",
                         crs_or_icans_dex_given_y_n = "Dexamethasone Use (CRS or ICANS)",
                         crs_and_icans_dex_given_y_n = "Dexamethasone Use (CRS and ICANS)",
                         total_cumulative_dose_d_1_d_30_days = "Cumulative steroids received during first 30 days",
                         # proteasome = "Refractory to Proteasome Inhibitors",
                         # lenalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Lenalidomide",
                         # bortezomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Bortezomib",
                         # carfilzomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Carfilzomib",
                         # pomalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Pomalidomide",
                         # dara = "Refractory to Daratumumab or Isatuximab",
                         # immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
                         # tripleref= "Triple refractory", pentaref= "Penta refractory",
                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese",
                         hospital_admit_y_n = "Required hospitalization",
                         peak_alc = "Peak ALC",
                         # peak_alc_grouping = "Peak ALC between days 8 and 19 - from column CC - seems wrong",
                         peak_alc_grouping_recoded = "Peak ALC ≥3.0 (recoded)",
                         alc_treated = "Lymphocytosis treated for peak ALC ≥3.0",
                         CRS_any = "Any CRS", crs_highest_grade = "Max CRS grade (0-5)",
                         CRS_gradecat2 = "CRS Grade 2+ (including no CRS)", 
                         CRS_gradecat3 = "CRS Grade 3+ (including no CRS)",
                         gr2_CRS = "CRS Grade 2+", gr3_CRS = "CRS Grade 3+",
                         
                         ICANS_any = "Any ICANS", icans_highest_grade = "Max ICANS grade (0-5)",
                         ICANS_gradecat2 = "ICANS Grade 2+ (including no ICANS)", 
                         ICANS_gradecat3 = "ICANS Grade 3+ (including no ICANS)", 
                         gr2_ICANS = "ICANS Grade 2+", gr3_ICANS = "ICANS Grade 3+",
                         
                         day_of_onset_crs_relative_to_infusion = "Day of onset of CRS relative to infusion",
                         # day_of_max_crs_relative_to_infusion = "Day of Max CRS (relative to infusion)",
                         crs_duration_days = "Duration of CRS (days)",
                         day_of_onset_icans_relative_to_infusion = "Day of onset of ICANS relative to infusion",
                         # day_of_icans_highest_grade_relative_to_infusion = "Day of Max ICANS (relative to infusion)",
                         icans_duration_days = "Duration of ICANS (days)",
                         nint_y_n = "NINT (Parkinsonian + CNP)",
                         nint_type = "NINT type",
                         updated_dnt_parkinson_yn = "Parkinsonian NT",
                         parkinsonian_neurotoxicity_duration_days = "Parkinsonian NT duration (days)",
                         updated_dnt_parkinsonresolved_yn = "Parkinsonian NT resolved",
                         day_of_onset_parkinsonian_relative_to_infusion = "Day of onset of Parkinsonian NT relative to infusion",
                         updated_dnt_cnp_yn = "CNP Neurotoxicity",
                         updated_dnt_cnpresolved_yn = "CNP Neurotoxicity resolved",
                         cnp_duration_days = "CNP Neurotoxicity duration (days)",
                         day_of_onset_cnp_relative_to_infusion = "Day of onset of CNP relative to infusion",
                         
                         day_of_onset_nint_relative_to_infusion = "Day of onset of NINT relative to infusion (CNP+PK)",
                         
                         nint_ivig_given = "IVIG Use (NINT)",
                         nint_tx_dex_y_n = "Dexamethasone Use (NINT) - column DS",
                         any_infection = "Any infection",
                         any_sevinfection = "Any severe infection",
                         severe_infection = "Infection severity",
                         severity_infection = "Infection",
                         # parkinsonian_neurotoxicity_y_n = "Parkinsonian Neurotoxicity",
                         # other_delayed_non_parkinsonian_neurologic_toxicity_y_n =
                         #   "Other/Delayed Non-Parkinsonian Neurologic Toxicity",
                         # delayed_neuro_type = "Delayed Neurotoxicity Type",
                         # hlh = "HLH", hlh_hlh_like_toxicities = "HLH/HLH-Like Toxicities?",
                         # overall_hlh = "Combined HLHs",
                         # tbv = "TBV", whole_blood_processed_m_l = "Whole blood processed (mL)",
                         # final_collection_volume_m_l = "Final collection volume (mL)",
                         # tbv_processed = "TBV processed",
                         # access_type = "Access type", total_bags = "Total bags",
                         # run_time_min = "Run time (min)",
                         # time_from_apheresis_to_car_t_infusion_days = "Time from apheresis to CAR-T infusion (days)",
                         # total_dose_volume_m_l = "Total dose volume (mL)",
                         # carvykti_cell_dose = "Total cell dose (million cells)",
                         updated_cartchar_infusion_dose = "CAR-T infusion dose",
                         # best_ORRcollapsed = "Best ORR at ≤ 12 months",
                         updated_outcomes_resp_d30 = "Response at day 30 (Gabe)",
                         response_d30 = "Response at day 30",
                         response_d30_v2 = "Day 30 Response - Death as PD",
                         ORR_30days = "Day 30 ORR", CRorbetter_30days = "Day 30 CR or better",
                         
                         updated_outcomes_resp_d90 = "Response at day 90 (Gabe)",
                         response_d90 = "Response at day 90",
                         response_d90_v2 = "Day 90 Response - Death as PD",
                         ORR_90days = "Day 90 ORR", CRorbetter_90days = "Day 90 CR or better",
                         
                         d_30_non_relapse_mortality = "30-day non-relapse mortality",
                         car_hematotox_score_aph = "CAR-HEMATOTOX score at apheresis",
                         car_hematotox_score_aph_cat = "CAR-HEMATOTOX score at apheresis (cat)",
                         car_hematotox_score_clear = "CAR-HEMATOTOX score at clearance",
                         car_hematotox_score_clear_cat = "CAR-HEMATOTOX score at clearance (cat)",

                         best_response_in90days = "Best response in first 90 days",
                         best_response = "Best overall response",
                         best_ORR = "Best overall ORR response",
                         best_CRorbetter = "Best overall CR or better response"
)

```
<br>


# Tables

```{r infused}
# cart3 %>%
#   select(`infused?` = notinfused) %>%
#   tbl_summary(missing = "no") %>%
#   bold_labels() %>% add_stat_label()
# cart3 %>% select(mrn,carvykti_cell_dose,
#                  updated_cartchar_infusion_dose) %>% filter(is.na(updated_cartchar_infusion_dose))
```

## Table 1. Patient baseline characteristics
```{r Table 1}
cart3 %>%
  select(age_d0, 
         time_since_diagnosis_to_d0_years,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone - IQR**")

cart3 %>%
  select(age_d0, agecat, #male_sex, 
         sex_m_f, race,
         ecog_performance_status, ecog_cat,
         os_from_infusion_months,
         time_since_diagnosis_to_d0_years,
         # extramedullary_disease_y_n,
         updated_bximag_imaging_emd_yn_preinf,
         cytogenetic_risk,
         # r_iss_staging_2,
         updated_r_iss,
         number_of_prior_therapies,
         number_prior_lines_therapy,
         prior_transplant, prior_auto_sct_y_n, prior_allo_sct_y_n,
         bm_bx_pre_bridging_60_percent_plasma_cells,
         scope_mm,
         bridging_therapy_y_n,
         bridging_type,
         past_exposure_to_bcma_y_n,
         car_hematotox_score_aph, car_hematotox_score_aph_cat,
         car_hematotox_score_clear, car_hematotox_score_clear_cat,
         ivig_given_y_n,
         # carvykti_cell_dose,
         updated_cartchar_infusion_dose,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              type = list(
                c(car_hematotox_score_aph,
                  all_dichotomous())
                ~"categorical",
                c(number_of_prior_therapies,
                  updated_cartchar_infusion_dose) ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              digits = all_continuous() ~ 1
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**")
```
One patient has a missing cell dose in Gabe's data which recorded = 6e+05 in the prophyl data. Gabe verified it and I fixed it (0.6).

<br>

## Table 2. Safety
### CRS/ICANS
```{r}
# breaka #for IQR??
cart3 %>%
  select(peak_alc,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone - IQR**")


cart3 %>%
  select(hospital_admit_y_n,
         peak_alc, peak_alc_grouping_recoded,
         # peak_alc_grouping, 
         alc_treated,
         crs_highest_grade, CRS_any, 
         CRS_gradecat2, CRS_gradecat3,
         gr2_CRS, gr3_CRS,
         day_of_onset_crs_relative_to_infusion, #crs_d,
         # day_of_max_crs_relative_to_infusion,
         crs_duration_days, 
         crs_toci_given, #crs_number_of_toci_doses,
         crs_tx_dex_y_n,
         crs_anakinra_given,
         crs_emapalumab_given,
         # crs_days_of_tx_dex, crs_tx_dex_given,
         # crs_days_of_anakinra, crs_other_therapies,

         icans_highest_grade, ICANS_any,
         ICANS_gradecat2, ICANS_gradecat3,
         gr2_ICANS, gr3_ICANS,
         day_of_onset_icans_relative_to_infusion, #icans_d,
         # day_of_icans_highest_grade_relative_to_infusion,
         icans_duration_days, 
         icans_tx_dex_y_n,
         icans_anakinra_given, 
         # icans_days_of_tx_dex, icans_tx_dex_given,
         #icans_days_of_anakinra, icans_other_therapies,
         crs_or_icans_dex_given_y_n,
         crs_and_icans_dex_given_y_n,
         # crs_icans_days_of_tx_dex, crs_icans_dex_given,
         total_cumulative_dose_d_1_d_30_days,
         ppx_dex_cohort_y_n
         ) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              type = list(c(all_dichotomous()) ~ "categorical",
                          c(crs_duration_days, day_of_onset_icans_relative_to_infusion,
                            icans_duration_days) ~ "continuous")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**")
```
<br>

### NINT
```{r}
cart3 %>%
  select(updated_dnt_parkinson_yn,
         updated_dnt_parkinsonresolved_yn,
         day_of_onset_parkinsonian_relative_to_infusion, 
         updated_dnt_cnp_yn,
         updated_dnt_cnpresolved_yn,
         day_of_onset_cnp_relative_to_infusion,
         
         
         nint_y_n, #nint_type,
         day_of_onset_nint_relative_to_infusion, #nint_d,
         # parkinsonian_neurotoxicity_yes_no,
         
         nint_tx_dex_y_n, #nint_days_of_tx_dex, nint_tx_dex_given,
         nint_ivig_given, #nint_other_therapies,
         ppx_dex_cohort_y_n
         ) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              type = list(c(all_dichotomous()) ~ "categorical",
                          c(day_of_onset_parkinsonian_relative_to_infusion, 
                            day_of_onset_cnp_relative_to_infusion,
                            day_of_onset_nint_relative_to_infusion) ~ "continuous")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**")
```


## In response to comment regarding CRS incidence and severity between both cohorts subgrouped based on clearance ferritin (<650 vs 650-2000 vs >2000)
```{r}
cart3 %>%
  filter(clearance_ferritin == "< 650") %>% 
  mutate(ppx_dex_cohort_y_n = case_when(
    ppx_dex_cohort_y_n == "Yes"        ~ "Recieved prophy dex",
    ppx_dex_cohort_y_n == "No"         ~ "Did not recieved prophy dex"
  )) %>% 
  select(crs_highest_grade, CRS_any, 
         CRS_gradecat2, CRS_gradecat3,
         gr2_CRS, gr3_CRS,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              type = list(c(all_dichotomous()) ~ "categorical")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>% 
  modify_header(label ~ "**Cohort =<br> Clearance ferritin group <650**") %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Clearance ferritin group <650**")

cart3 %>%
  filter(clearance_ferritin == "650 - 2000") %>% 
  mutate(ppx_dex_cohort_y_n = case_when(
    ppx_dex_cohort_y_n == "Yes"        ~ "Recieved prophy dex",
    ppx_dex_cohort_y_n == "No"         ~ "Did not recieved prophy dex"
  )) %>% 
  select(crs_highest_grade, CRS_any, 
         CRS_gradecat2, CRS_gradecat3,
         gr2_CRS, gr3_CRS,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              type = list(c(all_dichotomous()) ~ "categorical")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_header(label ~ "**Cohort =<br> Clearance ferritin group 650 - 2000**") %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Clearance ferritin group 650 - 2000**")

cart3 %>%
  filter(clearance_ferritin == "> 2000") %>% 
  mutate(ppx_dex_cohort_y_n = case_when(
    ppx_dex_cohort_y_n == "Yes"        ~ "Recieved prophy dex",
    ppx_dex_cohort_y_n == "No"         ~ "Did not recieved prophy dex"
  )) %>% 
  select(crs_highest_grade, CRS_any, 
         CRS_gradecat2, CRS_gradecat3,
         gr2_CRS, gr3_CRS,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              type = list(c(all_dichotomous()) ~ "categorical")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_header(label ~ "**Cohort =<br> Clearance ferritin group > 2000**") %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Clearance ferritin group > 2000**")
```
<br>

## Table 3. Efficacy/response
```{r table 2 outcome}
cart3 %>%
  select(any_infection, any_sevinfection,
         severity_infection, # severe_infection, 
         # updated_outcomes_resp_d30,
         # response_d30, 
         response_d30_v2,
         ORR_30days, CRorbetter_30days, 
         # updated_outcomes_resp_d90,
         # response_d90, 
         response_d90_v2,
         ORR_90days, CRorbetter_90days, 
         best_response_in90days, best_response, 
         best_ORR, best_CRorbetter,
         updated_day_of_prog_relative_to_infusion,

         updated_mortality,
         updated_day_of_death_relative_to_infusion,

         d_30_non_relapse_mortality,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              type = list(
                c(all_dichotomous())
                ~ "categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              digits = all_continuous() ~ 1#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**")
```
For "Emapalumab Use (CRS)", I am assuming the use of Emapalumab is for CRS as the name of the variable is "CRS Other Therapies". 
I coded "No" for all the patients with CRS any grade that didn't receive Emapalumab.    

crs_or_icans_dex_given_y_n "No" are coded so both use of Dex for CRS and ICANS be "No" (if only 1 is "No", then is coded NA).   
Same for crs_and_icans_dex_given_y_n but coded as both use of Dex for CRS and ICANS be "Yes" to ve coded "Yes".   

```{r}
cart3 %>%
  filter(updated_mortality == "Yes") %>% 
  select(`Cause of death` = updated_mortality_cause) %>% 
  tbl_summary() %>% 
  bold_labels() %>%
  add_stat_label()

# cart3 %>%
#   filter(!is.na(updated_outcomes_prog_dt)) %>%
#   select(mrn,updated_outcomes_prog_dt, updated_day_of_prog_relative_to_infusion,
#          starts_with("updated_outcomes_resp_")) %>%
#   arrange(updated_day_of_prog_relative_to_infusion)
```



```{r death check}

# death_dat <- cart3 %>%
#   # filter(updated_mortality == "Y") %>%
#   # filter((!is.na(date_of_mortality))) %>%
#   select(mrn, mortality,
#          date_of_mortality,
#          # day_of_death_relative_to_infusion,
#          # updated_outcomes_resp_d30,
#          updated_mortality,
#          # updated_day_of_death_relative_to_infusion,
#          updated_mortality_dt, , date_of_last_visit_contact, updated_vitalstatus_dt)
# 
# cart3 %>%
#   filter(mortality == "Yes") %>%
#   filter((!is.na(date_of_mortality))) %>%
#   select(mrn, mortality,
#          # day_of_death_relative_to_infusion,
#          updated_outcomes_resp_d30,
#          updated_mortality,
#          # updated_day_of_death_relative_to_infusion,
#          updated_mortality_dt, date_of_mortality, date_of_last_visit_contact)
```

# Survival
## OS
```{r KM OS}
ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ 1,
                   data=cart3),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(os_from_infusion_months, os_event) ~ ppx_dex_cohort_y_n,
                   data=cart3),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

Median OS in months
```{r}
survfit(Surv(time = cart3$os_from_infusion_months,
                   event = cart3$os_event) ~ 1,
              data = cart3) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  ) %>% add_nevent() %>% add_n()
survfit(Surv(time = cart3$os_from_infusion_months,
                   event = cart3$os_event) ~ ppx_dex_cohort_y_n,
              data = cart3) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  ) %>% add_nevent() %>% add_n()

list(
  survfit(Surv(time = cart3$os_from_infusion_months,
               event = cart3$os_event) ~ 1,
          data = cart3),
  survfit(Surv(time = cart3$os_from_infusion_months,
               event = cart3$os_event) ~ ppx_dex_cohort_y_n,
          data = cart3)
) %>% 
  tbl_survfit(times = c(6, 12),
              label_header = "**OS Rate at {time} Months**")

```

## PFS
```{r KM PFS}
ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ 1,
                   data=cart3),
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ ppx_dex_cohort_y_n,
                   data=cart3),
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

Median PFS in months
```{r}
survfit(Surv(time = cart3$pfs_from_infusion_months,
                   event = cart3$pfs_event) ~ 1,
              data = cart3) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  ) %>% add_nevent() %>% add_n()
survfit(Surv(time = cart3$pfs_from_infusion_months,
                   event = cart3$pfs_event) ~ ppx_dex_cohort_y_n,
              data = cart3) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  ) %>% add_nevent() %>% add_n()

list(
  survfit(Surv(time = cart3$pfs_from_infusion_months,
               event = cart3$pfs_event) ~ 1,
          data = cart3),
  survfit(Surv(time = cart3$pfs_from_infusion_months,
               event = cart3$pfs_event) ~ ppx_dex_cohort_y_n,
          data = cart3)
) %>% 
  tbl_survfit(times = c(6, 12),
              label_header = "**PFS Rate at {time} Months**")

```


<!-- # Labs -->
<!-- ```{r} -->
<!-- cart3 %>% -->
<!--   arrange(pt_identifier, desc(any_infection)) %>%  -->
<!--   distinct(pt_identifier, .keep_all = TRUE) %>%  -->
<!--   select(ig_g_day_5, ig_a_day_5, ig_m_day_5, -->
<!--          wbc_day_5, anc_day_5_k_ul, -->
<!--          # `Eos day -5 (k/ul)`, `Monos day -5 (k/ul)`,  -->
<!--          # `CD3 apheresis`, `CD56 apheresis`,  -->
<!--          cd4_apheresis, cd8_apheresis, -->
<!--          cd19_apheresis,  -->
<!--          ig_g_day_90, ig_a_day_90, ig_m_day_90, -->
<!--          wbc_day_90, anc_day_90, -->
<!--          # `Eos day +90`, `Monos day +90`, -->
<!--          # `CD3 day +90`, `CD56 day +90`,  -->
<!--          cd4_day_90, cd8_day_90, -->
<!--          cd19_day_90, ht_score, -->
<!--          ppx_dex_cohort_y_n) %>%  -->
<!--   tbl_summary(by = ppx_dex_cohort_y_n, -->
<!--               statistic=list(all_continuous() ~ "{median} ({min}, {max})"),  -->
<!--               digits = all_continuous() ~ 1) %>%  -->
<!--   add_p() %>% bold_labels() %>%  -->
<!--   add_stat_label() %>%  -->
<!--   modify_header(update = c(stat_1, stat_2) ~ "**{level}**, N = {n}") %>% -->

<!--   modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**") -->
<!-- ``` -->

<!-- # Figures -->

<!-- ## Figure S1. Inflammatory markers after cilta-cel -->


<!-- ```{r Figure 2. Inflammatory markers after cilta-cel, fig.height=12} -->
<!-- LDH <- fig_dat %>%  -->
<!--   select(pt_identifier, starts_with("ldh_")) %>%  -->
<!--   pivot_longer(cols = -c(pt_identifier)) %>%  -->
<!--   mutate(name = str_remove(name, "_k_ul|_k_u_l"), -->
<!--          day = case_when( -->
<!--            str_detect(name, "apheresis")            ~ "-28", -->
<!--            str_detect(name, "pretreatment")         ~ "-28", -->
<!--            str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2]) -->
<!--          ),  -->
<!--          day = case_when( -->
<!--            day == 5                                 ~ "-5", -->
<!--            TRUE                                     ~ day -->
<!--          ), -->
<!--          day = factor(day, levels = c("-28", "-5", "0",  -->
<!--                                       "7", "14", "21", "30", "90", "180"))) %>%  -->
<!--   ggplot(aes(x=day, y=value)) +  -->
<!--   geom_boxplot() +  -->
<!--   xlab("Days") + ylab("LDH (log2 scale)") +  -->
<!--   theme_classic() + ggtitle("LDH") +  -->
<!--   scale_y_continuous(trans = "log2") + -->
<!--   stat_compare_means(label.x = 1.2 , label.y.npc = 0.95, -->
<!--                      size = 5 -->
<!--                      # aes(label = paste0("p = ", ..p.format..)) -->
<!--   #                  aes( -->
<!--   # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other") -->
<!--   ) -->


<!-- # cart1$`Ferritin day +7`[cart1$`Ferritin day +7`==">33511"] <- /33511 -->
<!-- # cart1$`Ferritin day +7` <- as.numeric(cart1$`Ferritin day +7`) -->
<!-- Ferritin <- fig_dat %>%  -->
<!--   select(pt_identifier, starts_with("ferritin_"), -ferritin_score) %>%  -->
<!--   pivot_longer(cols = -c(pt_identifier)) %>%  -->
<!--   mutate(name = str_remove(name, "_k_ul|_k_u_l"), -->
<!--          day = case_when( -->
<!--            str_detect(name, "apheresis")            ~ "-28", -->
<!--            str_detect(name, "pretreatment")         ~ "-28", -->
<!--            str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2]) -->
<!--          ),  -->
<!--          day = case_when( -->
<!--            day == 5                                 ~ "-5", -->
<!--            TRUE                                     ~ day -->
<!--          ), -->
<!--          day = factor(day, levels = c("-28", "-5", "0",  -->
<!--                                       "7", "14", "21", "30", "90", "180"))) %>%  -->
<!--   ggplot(aes(x=day, y=value)) +  -->
<!--   geom_boxplot() +  -->
<!--   xlab("Days") + ylab("Ferritin (log2 scale)") +  -->
<!--   theme_classic() + ggtitle("Ferritin") +  -->
<!--   scale_y_continuous(trans = "log2") + -->
<!--   stat_compare_means(label.x = 1.2 , label.y.npc = 0.95, -->
<!--                      size = 5 -->
<!--                      # aes(label = paste0("p = ", ..p.format..)) -->
<!--   #                  aes( -->
<!--   # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other") -->
<!--   ) -->



<!-- # cart1$`CRP Pre-Leukapheresis`[cart1$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07 -->
<!-- # cart1$`CRP Pre-Leukapheresis` <- as.numeric(cart1$`CRP Pre-Leukapheresis`) -->
<!-- # cart1$`CRP day +14`[cart1$`CRP day +14`=="<0.03"] <- 0.07 -->
<!-- # cart1$`CRP day +14` <- as.numeric(cart1$`CRP day +14`) -->
<!-- # cart1$`CRP day +21`[cart1$`CRP day +21`=="<0.03"] <- 0.07 -->
<!-- # cart1$`CRP day +21` <- as.numeric(cart1$`CRP day +21`) -->
<!-- # cart1$`CRP day +30`[cart1$`CRP day +30`=="<0.03"] <- 0.07 -->
<!-- # cart1$`CRP day +30` <- as.numeric(cart1$`CRP day +30`) -->
<!-- CRP <- fig_dat %>%  -->
<!--   select(pt_identifier, starts_with("crp_"), -crp_score) %>%  -->
<!--   pivot_longer(cols = -c(pt_identifier)) %>%  -->
<!--   mutate(name = str_remove(name, "_k_ul|_k_u_l"), -->
<!--          day = case_when( -->
<!--            str_detect(name, "apheresis")            ~ "-28", -->
<!--            str_detect(name, "pretreatment")         ~ "-28", -->
<!--            str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2]) -->
<!--          ),  -->
<!--          day = case_when( -->
<!--            day == 5                                 ~ "-5", -->
<!--            TRUE                                     ~ day -->
<!--          ), -->
<!--          day = factor(day, levels = c("-28", "-5", "0",  -->
<!--                                       "7", "14", "21", "30", "90", "180"))) %>%  -->
<!--   ggplot(aes(x=day, y=value)) +  -->
<!--   geom_boxplot() +  -->
<!--   xlab("Days") + ylab("CRP (log2 scale)") +  -->
<!--   theme_classic() + ggtitle("CRP") +  -->
<!--   scale_y_continuous(trans = "log2") + -->
<!--   stat_compare_means(label.x = 1.2, label.y.npc = 0.95, -->
<!--                      size = 5 -->
<!--                      # aes(label = paste0("p = ", ..p.format..)) -->
<!--   #                  aes( -->
<!--   # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other") -->
<!--   ) -->

<!-- (LDH) / -->
<!-- (Ferritin) / -->
<!-- (CRP)+ -->
<!-- plot_annotation(tag_levels = "A") & -->
<!--   theme(plot.tag = element_text(size = 17), -->
<!--         text = element_text(size = 16)) -->

<!-- # ggsave("Figure S1 Inflammatory markers after cilta-cel_03-12-25_300dpi.pdf", -->
<!-- #        width = 6, -->
<!-- #        height = 10) -->


<!-- ggsave("Figure S1 Inflammatory markers after cilta-cel_600dpi_1column_compress.tiff", -->
<!--        dpi = 600, units = "in", -->
<!--        width = 8, -->
<!--        height = 11, compression = "lzw") -->





<!-- ``` -->

<!-- ## Figure 2. Cellular and humoral immune reconstitution after cilta-cel -->
<!-- ```{r timeserie, fig.width=12, fig.height=12} -->
<!-- # WBC -->
<!-- val <- fig_dat %>% reframe(wbc_apheresis = MedianCI(wbc_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   wbc_day_5 = MedianCI(wbc_day_5, conf.level = 0.95, na.rm = TRUE), -->
<!--                   wbc_day_0_k_u_l = MedianCI(wbc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE), -->
<!--                   wbc_day_7 = MedianCI(wbc_day_7, conf.level = 0.95, na.rm = TRUE), -->
<!--                   wbc_day_14 = MedianCI(wbc_day_14, conf.level = 0.95, na.rm = TRUE), -->
<!--                   wbc_day_21 = MedianCI(wbc_day_21, conf.level = 0.95, na.rm = TRUE), -->
<!--                   wbc_day_30 = MedianCI(wbc_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   wbc_day_90 = MedianCI(wbc_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   wbc_day_180 = MedianCI(wbc_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180) -->
<!-- WBC_fig <- -->
<!--   data.frame(timepoints, -->
<!--              t(val)) -->

<!-- WBC_fig <- -->
<!--   WBC_fig %>% -->
<!--   ggplot(aes(x = timepoints, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") +  -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median WBC") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
<!--     labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180") -->
<!--   ) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- # ANC -->
<!-- val <- fig_dat %>% reframe(anc_apheresis = MedianCI(anc_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   anc_day_5_k_ul = MedianCI(anc_day_5_k_ul, conf.level = 0.95, na.rm = TRUE), -->
<!--                   anc_day_0_k_u_l = MedianCI(anc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE), -->
<!--                   anc_day_7 = MedianCI(anc_day_7, conf.level = 0.95, na.rm = TRUE), -->
<!--                   anc_day_14 = MedianCI(anc_day_14, conf.level = 0.95, na.rm = TRUE), -->
<!--                   anc_day_21 = MedianCI(anc_day_21, conf.level = 0.95, na.rm = TRUE), -->
<!--                   anc_day_30 = MedianCI(anc_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   anc_day_90 = MedianCI(anc_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   anc_day_180 = MedianCI(anc_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180) -->
<!-- ANC_fig <- -->
<!--   data.frame(timepoints, -->
<!--              t(val)) -->


<!-- ANC_fig <- ANC_fig %>%  -->
<!--   ggplot(aes(x = timepoints, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") +  -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median ANC") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
<!--     labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180") -->
<!--   ) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- # HB -->
<!-- val <- fig_dat %>% reframe(hb_apheresis = MedianCI(hb_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   hb_day_5 = MedianCI(hb_day_5, conf.level = 0.95, na.rm = TRUE), -->
<!--                   hb_day_0_k_u_l = MedianCI(hb_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE), -->
<!--                   hb_day_7 = MedianCI(hb_day_7, conf.level = 0.95, na.rm = TRUE), -->
<!--                   hb_day_14 = MedianCI(hb_day_14, conf.level = 0.95, na.rm = TRUE), -->
<!--                   hb_day_21 = MedianCI(hb_day_21, conf.level = 0.95, na.rm = TRUE), -->
<!--                   hb_day_30 = MedianCI(hb_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   hb_day_90 = MedianCI(hb_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   hb_day_180 = MedianCI(hb_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180) -->
<!-- Hb_fig <- -->
<!--   data.frame(timepoints, -->
<!--              t(val)) -->

<!-- Hb_fig <- Hb_fig %>%  -->
<!--   ggplot(aes(x = timepoints, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") +  -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median Hb") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
<!--     labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180") -->
<!--   ) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- # ALC -->
<!-- val <- fig_dat %>% reframe(alc_apheresis = MedianCI(alc_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   alc_day_5_k_ul = MedianCI(alc_day_5_k_ul, conf.level = 0.95, na.rm = TRUE), -->
<!--                   alc_day_0_k_u_l = MedianCI(alc_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE), -->
<!--                   alc_day_7 = MedianCI(alc_day_7, conf.level = 0.95, na.rm = TRUE), -->
<!--                   alc_day_14 = MedianCI(alc_day_14, conf.level = 0.95, na.rm = TRUE), -->
<!--                   alc_day_21 = MedianCI(alc_day_21, conf.level = 0.95, na.rm = TRUE), -->
<!--                   alc_day_30 = MedianCI(alc_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   alc_day_90 = MedianCI(alc_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   alc_day_180 = MedianCI(alc_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180) -->
<!-- ALC_fig <- -->
<!--   data.frame(timepoints, -->
<!--              t(val)) -->

<!-- ALC_fig <- ALC_fig %>%  -->
<!--   ggplot(aes(x = timepoints, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") +  -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median ALC") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
<!--     labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180") -->
<!--   ) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- # Plt -->
<!-- val <- fig_dat %>% reframe(plt_apheresis = MedianCI(plt_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   plt_day_5_k_ul = MedianCI(plt_day_5_k_ul, conf.level = 0.95, na.rm = TRUE), -->
<!--                   plt_day_0_k_u_l = MedianCI(plt_day_0_k_u_l, conf.level = 0.95, na.rm = TRUE), -->
<!--                   plt_day_7 = MedianCI(plt_day_7, conf.level = 0.95, na.rm = TRUE), -->
<!--                   plt_day_14 = MedianCI(plt_day_14, conf.level = 0.95, na.rm = TRUE), -->
<!--                   plt_day_21 = MedianCI(plt_day_21, conf.level = 0.95, na.rm = TRUE), -->
<!--                   plt_day_30 = MedianCI(plt_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   plt_day_90 = MedianCI(plt_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   plt_day_180 = MedianCI(plt_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- timepoints <- c(-28, -5, 0, 7, 14, 21, 30, 90, 180) -->
<!-- Plt_fig <- -->
<!--   data.frame(timepoints, -->
<!--              t(val)) -->

<!-- Plt_fig <- Plt_fig %>%  -->
<!--   ggplot(aes(x = timepoints, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") +  -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median Plt") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, -5, 0, 7, 14, 21, 30, 90, 180), -->
<!--     labels = c("Apheresis","-5 ", "0", "7", "14", "21", "30", "90", "180") -->
<!--   ) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- # IgG -->
<!-- timepoints2 <- c(-28, -5, 30, 90, 180) -->
<!-- val <- fig_dat %>% reframe(ig_g_apheresis = MedianCI(ig_g_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   ig_g_day_5 = MedianCI(ig_g_day_5, conf.level = 0.95, na.rm = TRUE), -->
<!--                   ig_g_day_30 = MedianCI(ig_g_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   ig_g_day_90 = MedianCI(ig_g_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   ig_g_day_180 = MedianCI(ig_g_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- IgG_fig <- -->
<!--   data.frame(timepoints2, -->
<!--              t(val)) -->

<!-- IgG_fig <- IgG_fig %>%  -->
<!--   ggplot(aes(x = timepoints2, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") + -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median IgG") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, -5, 30, 90, 180), -->
<!--     labels = c("Apheresis", "-5 ", "30", "90", "180")) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- # CD4 -->
<!-- timepoints3 <- c(-28, 30, 90, 180) -->
<!-- val <- fig_dat %>% reframe(cd4_apheresis = MedianCI(cd4_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd4_day_30 = MedianCI(cd4_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd4_day_90 = MedianCI(cd4_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd4_day_180 = MedianCI(cd4_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- CD4_fig <- -->
<!--   data.frame(timepoints3, -->
<!--              t(val)) -->

<!-- CD4_fig <- CD4_fig %>%  -->
<!--   ggplot(aes(x = timepoints3, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") +  -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median CD4") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, 30, 90, 180), -->
<!--     labels = c("Apheresis", "30", "90", "180") -->
<!--   ) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- #CD8 -->
<!-- timepoints3 <- c(-28, 30, 90, 180) -->
<!-- val <- fig_dat %>% reframe(cd8_apheresis = MedianCI(cd8_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd8_day_30 = MedianCI(cd8_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd8_day_90 = MedianCI(cd8_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd8_day_180 = MedianCI(cd8_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- CD8_fig <- -->
<!--   data.frame(timepoints3, -->
<!--              t(val)) -->

<!-- CD8_fig <- CD8_fig %>%  -->
<!--   ggplot(aes(x = timepoints3, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") +  -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median CD8") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, 30, 90, 180), -->
<!--     labels = c("Apheresis", "30", "90", "180") -->
<!--   ) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- #CD19 -->
<!-- timepoints3 <- c(-28, 30, 90, 180) -->
<!-- val <- fig_dat %>% reframe(cd19_apheresis = MedianCI(cd19_apheresis, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd19_day_30 = MedianCI(cd19_day_30, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd19_day_90 = MedianCI(cd19_day_90, conf.level = 0.95, na.rm = TRUE), -->
<!--                   cd19_day_180 = MedianCI(cd19_day_180, conf.level = 0.95, na.rm = TRUE)) -->
<!-- CD19_fig <- -->
<!--   data.frame(timepoints3, -->
<!--              t(val)) -->

<!-- CD19_fig <- CD19_fig %>%  -->
<!--   ggplot(aes(x = timepoints3, y = X1, group = 1)) +  -->
<!--   geom_line(col = "blue") +  -->
<!--   xlab("Days relative to infusion") +  -->
<!--   ylab("Median CD19") +  -->
<!--   theme_classic() +  -->
<!--   geom_ribbon(aes(ymin = X2, ymax = X3), alpha = 0.1) +  -->
<!--   scale_x_continuous( -->
<!--     breaks = c(-28, 30, 90, 180), -->
<!--     labels = c("Apheresis", "30", "90", "180") -->
<!--   ) + -->
<!--   theme(text = element_text(size = 8)) -->

<!-- (WBC_fig | ANC_fig | CD4_fig) / -->
<!--   (Hb_fig | ALC_fig | CD8_fig) / -->
<!--   (Plt_fig | IgG_fig | CD19_fig) + -->
<!--   plot_annotation(tag_levels = "A") & -->
<!--   theme(plot.tag = element_text(size = 15), -->
<!--         axis.title = element_text(size = 13), -->
<!--         axis.text.y = element_text(size = 11), -->
<!--         axis.text.x = element_text(size = 8), -->
<!--         legend.title = element_text(size = 13), -->
<!--         legend.text = element_text(size = 11)) -->

<!-- ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel_600dpi_2column.tiff", -->
<!--        dpi = 600, units = "in", -->
<!--        width = 16, -->
<!--        height = 8) -->

<!-- # (WBC_fig | ANC_fig) / -->
<!-- #   (CD4_fig | Hb_fig) /  -->
<!-- #   (ALC_fig | CD8_fig) / -->
<!-- #   (Plt_fig | IgG_fig) /  -->
<!-- #   (CD19_fig | plot_spacer()) + -->
<!-- #   plot_annotation(tag_levels = "A") & -->
<!-- #   theme(plot.tag = element_text(size = 16), -->
<!-- #         axis.title = element_text(size = 16), -->
<!-- #         axis.text.y = element_text(size = 14), -->
<!-- #         axis.text.x = element_text(size = 13), -->
<!-- #         legend.title = element_text(size = 16), -->
<!-- #         legend.text = element_text(size = 14)) -->
<!-- #  -->
<!-- # ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel_600dpi_2column_.jpeg", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 16, -->
<!-- #        height = 13) -->




<!-- ``` -->
<!-- <br> -->













