---
title: Usage of Prophylactic Dexamethasone to Reduce Incidence and Severity of Toxicity
  after Ciltacabtagene autoleucel
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: kable
  word_document:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library, echo = FALSE}
library(tidyverse)
library(labelled)
library(gtsummary)
library(survminer)
library(survival)
theme_gtsummary_compact()
theme_set(theme_classic())
```


```{r load}
# The repository is saved here 
# Peres_Research/Myeloma/Analyses/Prophylactic Dexamethasone/Rproject/toxocity_prophylactic_dexamethasone
path <- fs::path("","Volumes","Peres_Research", "")

clinical <-
  readxl::read_xlsx(paste0(#path, 
                           here::here(), "/data/raw_data",
                           "/Carvykti Data Collection Current 8.20.26.xlsx"), 
                    na = c("NR", "NA", "Na", "unk", "Unk"),
                    skip = 1
                    ) %>% 
  janitor::clean_names()

# consortium <-
#   readxl::read_xlsx(paste0(#path, 
#                            here::here(), "/data/raw_data",
#                            "/dougas_prophy_dex_data_01-27-2026.xlsx"), 
#                     na = c("unk", "na")
#                     ) %>% 
#   janitor::clean_names()
# gabe_data <-
#   readxl::read_xlsx(paste0(#path, 
#                            here::here(), "/data/raw_data",
#                            "/dougas_prophy_dex_vitalstatus_response_data_02-18-2026.xlsx"), 
#                     na = c("unk")
#                     ) %>% 
#   janitor::clean_names()
```

```{r exploratory function}
# data <- clinical %>%
#   # select_if(~!is.numeric(.)) %>%
#   select_if(~!is.POSIXct(.))
# # data <- consortium %>%
# #   # select_if(~!is.numeric(.)) %>%
# #   select_if(~!is.POSIXct(.))
# 
# check_data <- function(data){
# 
#   for(i in 1:length(colnames(data))) {
# 
#     # if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
# 
#       # print(data[i])
#       print(colnames(data[i]))
#       print(str(data[[i]]))
#       print(table(data[[i]]))
#     # }
# 
#   }
# }
# 
# check_data(data)

```

```{r consortium cleaning}
# consortium1 <- consortium %>%
#   select(-c(outcomes_resp_d30, outcomes_resp_d90,
#             outcomes_resp_d180, outcomes_resp_d360,
#             outcomes_prog_dt, mortality,
#             mortality_dt, mortality_cause)) %>%
#   left_join(., gabe_data,
#             by = c("key_mrn", "key_ptid")) %>%
#   mutate(cartchar_infusion_dose = case_when(
#     cartchar_infusion_dose == 999999                   ~ 0.6,
#     TRUE                                               ~ cartchar_infusion_dose
#   )) %>%
#   mutate(r_iss = na_if(r_iss, "Unable to Calculate")) %>%
#   `colnames<-`(paste0("updated_", colnames(.)))
```

```{r verification function}
# data <- consortium1 %>%
#   # select_if(~!is.numeric(.)) %>%
#   select_if(~!is.POSIXct(.))

# check_data <- function(data){
#
#   for(i in 1:length(colnames(data))) {
#
#     # if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
#
#       # print(data[i])
#       print(colnames(data[i]))
#       print(str(data[[i]]))
#       print(table(data[[i]]))
#     # }
#
#   }
# }

# check_data(data[2:28])
```

```{r merge}
clinical <- clinical %>%
  # General ----
  # Fix letter case and missing
  mutate(across(c(where(is.character),
                  - c("nint_type",
                      "d_30", "d_90", "d_180", "d_365",
                      "bridging_response")),# c("tumor_bcma_expression"),
                ~ str_to_sentence(.) )) %>%
  # mutate(across(c(contains("vgpr"), "response_to_bridging_chemotherapy"
  #                 ),
  #               ~ str_to_upper(.) )) %>%
  mutate(across(where(is.character),
                ~ str_replace(., "^Unknown$", NA_character_))) #%>%
  # Merge----
  # inner_join(., consortium1, by = c("mrn" = "updated_key_mrn"))
```

```{r clinical cleaning}
cart <- clinical %>%
  # Demo----
  mutate(agecat = case_when(
    age_d0 < 70                                         ~ "< 70 years",
    age_d0 >= 70                                        ~ "≥ 70 years"
  ),
  agecat = factor(agecat, levels = c("< 70 years", "≥ 70 years"))
  ) %>%
  mutate(race_all = case_when(
    race == "W"                                         ~ "White",
    race == "B"                                         ~ "Black",
    race == "Api"                                       ~ "Asian/Pacific Islander",
    race == "O"                                         ~ "Other",
    TRUE                                                ~ race
  )) %>%
  mutate(race = case_when(
    race_all == "White"                                 ~ "White",
    race_all == "Black"                                 ~ "Black",
    race_all == "Asian/Pacific Islander" |
      race_all == "Other"                               ~ "Other",
    TRUE                                                ~ race_all
  )) |> 
  # Yes/No----
  mutate_at(c("ppx_dex_cohort_y_n",
              "ecog_performance_status_0_1_y_n",
              "hx_of_previous_malignancy_y_n",
              "extramedullary_disease_y_n",
              "past_exposure_to_bcma_y_n",
              "prior_cart_exposure",
              "bm_bx_pre_bridging_50_percent_plasma_cells",
              "bridging_therapy_y_n",
              "ivig_given_y_n",
              "hospital_admit_y_n",
              "crs_y_n",
              "crs_tx_dex_y_n",
              "crs_toci_given",
              "crs_anakinra_given",
              "crs_anakinra_given",
              "icans_y_n",
              "icans_tx_dex_y_n",
              "icans_anakinra_given",
              "icans_other_therapies",
              "crs_early_intervention_dex_y_n",
              "crs_early_intervention_toci_y_n",
              "nint_y_n",
              "nint_tx_dex_y_n",
              "nint_ivig_given",
              "nint_other_therapies",
              "ivig_ppx",
              "infectious_complications_90_day",
              "severe_infection",
              "other_g3_4_toxicities_y_n",
              "mortality",
              "d_30_non_relapse_mortality"),
            ~ case_when(
              . == "Y"                 ~ "Yes",
              . == "N"                 ~ "No",
              TRUE                     ~ .
            )) %>%
  # Sex categories----
  mutate(sex_m_f = case_when(
    sex_m_f == "M"                     ~ "Male",
    sex_m_f == "F"                     ~ "Female",
    TRUE                               ~ sex_m_f
  )) %>%
  mutate(male_sex = case_when(
    sex_m_f == "Male"                  ~ 1,
    sex_m_f == "Female"                ~ 0
  )) %>%

  # ECOG
  mutate(ecog_cat = case_when(
    ecog_performance_status == 0 |
      ecog_performance_status == 1     ~ "0-1",
    ecog_performance_status %in% c(2:4)  ~ "2-4"
  )) %>%

  # Disease ----
  mutate(r_iss_staging_2 = case_when(
    r_iss_staging_2 == 1               ~ "I",
    r_iss_staging_2 == 2               ~ "II",
    r_iss_staging_2 == 3               ~ "III",
    r_iss_staging_2 == "Unknown"       ~ NA_character_,
    TRUE                               ~ r_iss_staging_2
  )) %>%
  mutate(car_hematotox_score_aph_cat = case_when(
    car_hematotox_score_aph %in%
      c(0:3)                           ~ "0-3",
    car_hematotox_score_aph > 3        ~ "4+"
  )) %>%
  mutate(car_hematotox_score_clear_cat3plus = case_when(
    car_hematotox_score_clear %in%
      c(0:2)                           ~ "0-2",
    car_hematotox_score_clear > 2      ~ "3+"
  )) %>%
  mutate(car_hematotox_score_clear_cat4plus = case_when(
    car_hematotox_score_clear %in%
      c(0:3)                           ~ "0-3",
    car_hematotox_score_clear > 3      ~ "4+"
  )) %>%
  mutate(scope_mm = factor(scope_mm, levels = c("Low", "Intermediate", "High"))) |> 
  mutate(ivig_ppx = case_when(
    ivig_ppx == "N"                    ~ "No Prophylaxis",
    ivig_ppx == "Primary"              ~ "Primary Prophylaxis",
    ivig_ppx == "Secondary"            ~ "Secondary Prophylaxis",
    TRUE                               ~ ivig_ppx
  )) |> 
  mutate(peak_alc_grouping = case_when(
    peak_alc_grouping == 0             ~ "ALC ≥ 3",
    peak_alc_grouping == 1             ~ "ALC < 3",
    TRUE                               ~ as.character(peak_alc_grouping)
  )) %>%
  mutate(peak_alc_grouping_recoded = case_when(
    peak_alc >= 3                      ~ "ALC ≥ 3",
    peak_alc < 3                       ~ "ALC < 3",
    TRUE                               ~ as.character(peak_alc)
  )) %>%
  mutate(alc_treated = case_when(
    alc_treated == 0                   ~ "Not treated",
    alc_treated == 1                   ~ "Dexamethasone",
    alc_treated == 2                   ~ "Dexamethasone + Cyclophosphamide",
    TRUE                               ~ as.character(alc_treated)
  ))
```

```{r infusion}
cart <- cart %>%
  mutate(infused = case_when(
    !is.na(date_of_carvykti_d0)        ~ "Yes",
    TRUE                               ~ "No"
  ))
```


```{r treatment}
cart <- cart %>%
  mutate(dara = case_when(
    daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed == "Refractory"            
                                                                                  ~ "Yes",
    is.na(daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed)
                                                                                  ~ NA_character_,
    TRUE                                                                          ~ "No"
  ), .after = daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed) %>%
  mutate(proteasome = case_when(
    bortezomib_exposed_vs_refractory_vs_not_exposed == "Refractory" |
      carfilzomib_exposed_vs_refractory_vs_not_exposed == "Refractory"            ~ "Yes",
    bortezomib_exposed_vs_refractory_vs_not_exposed != "Refractory" |
      carfilzomib_exposed_vs_refractory_vs_not_exposed != "Refractory"            ~ "No"
  )) %>%
  mutate(immuno = case_when(
    lenalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" |
      pomalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory"           ~ "Yes",
    lenalidomide_exposed_vs_refractory_vs_not_exposed != "Refractory" |
      pomalidomide_exposed_vs_refractory_vs_not_exposed != "Refractory"           ~ "No"
  ), .after = pomalidomide_exposed_vs_refractory_vs_not_exposed) %>% 
  mutate(doubleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes"                                                             ~ "Yes",
    TRUE                                                                          ~ "No"
  ), .after = proteasome) %>%
  mutate(tripleref = case_when(
    proteasome == "Yes" &
      immuno == "Yes" &
      dara == "Yes"                                                               ~ "Yes",
    TRUE                                                                          ~ "No"
  )) %>% 
  mutate(pentaref = case_when(
    bortezomib_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      carfilzomib_exposed_vs_refractory_vs_not_exposed == "Refractory" &
      lenalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      pomalidomide_exposed_vs_refractory_vs_not_exposed == "Refractory" & 
      dara == "Yes"                                                               ~ "Yes",
    TRUE                                                                          ~ "No"
  )) |> 
  
  
  mutate(prior_transplant = case_when(
    prior_transplant == "N"            ~ "No",
    TRUE                               ~ prior_transplant
  )) %>%
  mutate(prior_auto_sct_y_n = case_when(
    prior_transplant == "No"           ~ "No",
    prior_transplant == "Y"          ~ "Y",
    prior_transplant == "Auto"         ~ "Yes (Auto)",
    prior_transplant == "Allo"         ~ "No"
  )) %>%
  mutate(prior_allo_sct_y_n = case_when(
    prior_transplant == "No"           ~ "No",
    prior_transplant == "Y"          ~ "Y",
    prior_transplant == "Auto"         ~ "No",
    prior_transplant == "Allo"         ~ "Yes (Allo)"
  )) %>%
  mutate(number_prior_lines_therapy_cat13 = case_when(
    number_of_prior_therapies %in% c(1:3)                 ~ "1-3",
    number_of_prior_therapies > 3                         ~ "4 or more"
  )) %>%
  mutate(number_prior_lines_therapy_cat12 = case_when(
    number_of_prior_therapies %in% c(1:2)                 ~ "1-2",
    number_of_prior_therapies > 2                         ~ "3 or more"
  )) %>%
  mutate(bridging_type = case_when(
    bridging_grouping == 0             ~ "Conventional chemoimmunotherapy",
    bridging_grouping == 1             ~ "GPRC5D-based regimen",
  )) %>%
  mutate(bridging_response_cat_vgpr = case_when(
    str_detect(bridging_response,
               "VGPR|CR")                                 ~ "VGPR or better",
    str_detect(bridging_response,
               "PR|SD|PD")                                ~ "PR/SD/PD",
    TRUE                                                  ~ bridging_response
  )) |> 
  mutate(bridging_response_cat_pr = case_when(
    str_detect(bridging_response,
               "PR|CR")                                   ~ "PR or better",
    str_detect(bridging_response,
               "SD|PD")                                   ~ "SD/PD",
    TRUE                                                  ~ bridging_response
  ), 
  bridging_response_cat_pr = factor(bridging_response_cat_pr),
  bridging_response_cat_pr = relevel(bridging_response_cat_pr, ref = "SD/PD")) |> 
  mutate(bridging_response_cat2pr = case_when(
    bridging_therapy_y_n == "No"                          ~ "No bridging",
    str_detect(bridging_response,
               "PR|CR")                                   ~ "PR or better",
    str_detect(bridging_response,
               "SD|PD")                                   ~ "SD/PD",
    TRUE                                                  ~ bridging_response
  )) |> 
  mutate(bridging_response_cat2vgpr = case_when(
    bridging_therapy_y_n == "No"                          ~ "No bridging",
    str_detect(bridging_response,
               "VGPR|CR")                                 ~ "VGPR or better",
    str_detect(bridging_response,
               "PR|SD|PD")                                ~ "PR/SD/PD",
    TRUE                                                  ~ bridging_response
  )) |> 
  mutate(crs_emapalumab_given = case_when(
    crs_other_therapies == "Emapalumab"                ~ "Yes",
    crs_y_n == "Yes"                                   ~ "No"
  )) %>%
  # mutate(crs_or_icans_dex_given_y_n = case_when(
  #   crs_tx_dex_y_n == "Yes"                            ~ "Yes",
  #   icans_tx_dex_y_n == "Yes"                          ~ "Yes",
  #   crs_tx_dex_y_n == "No" &
  #     icans_tx_dex_y_n == "No"                         ~ "No"
  # )) %>%
  # mutate(crs_and_icans_dex_given_y_n = case_when(
  #   crs_tx_dex_y_n == "Yes" &
  #     icans_tx_dex_y_n == "Yes"                        ~ "Yes",
  #   crs_tx_dex_y_n == "No" &
  #     icans_tx_dex_y_n == "No"                         ~ "No"
  # )) %>%
  mutate(nint_tx_dex_y_n = case_when(
    nint_tx_dex_y_n == "Yes"                           ~ "Yes",
    is.na(nint_tx_dex_y_n) &
      nint_y_n == "Yes"                                ~ "No"
  ))


```

```{r toxicities}
cart2 <- cart %>%
# CRS ----
  mutate(crs_any = ifelse(crs_highest_grade == 0, "No", "Yes"),
       crs_any2 = ifelse(crs_any == "No", 0, 1),
       crs_gradecat2 = case_when(
         crs_highest_grade == 0                        ~ "No CRS",
         crs_highest_grade == 1                        ~ "Grade 1",
         crs_highest_grade >= 2                        ~ "Grade 2+"),
       crs_gradecat2 = factor(crs_gradecat2, levels = c("No CRS", "Grade 1", "Grade 2+")),
       crs_gradecat3 = case_when(
         crs_highest_grade == 0                        ~ "No CRS",
         crs_highest_grade %in% c(1:2)                 ~ "Grade 1 or 2",
         crs_highest_grade >= 3                        ~ "Grade 3+"),
       crs_gradecat3 = factor(crs_gradecat3, levels = c("No CRS", "Grade 1 or 2", "Grade 3+"))
  ) %>%
  mutate(gr3_crs = case_when(
    crs_highest_grade %in% c(1:2)                      ~ "Grade <3",
    crs_highest_grade %in% c(3:5)                      ~ "Grade ≥3"
  )) %>%
  mutate(gr2_crs = case_when(
    crs_highest_grade %in% c(1)                        ~ "Grade <2",
    crs_highest_grade %in% c(2:5)                      ~ "Grade ≥2"
  )) %>%
  mutate(day_of_onset_crs_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = crs_day_of_onset) /
           duration(n =1, unit = "days")
  ) %>%
  # mutate(day_of_max_crs_relative_to_infusion =
  #          interval(start = date_of_carvykti_d0, end = date_of_max_crs) /
  #          duration(n =1, unit = "days")
  # ) %>%

  # ICANS ----
  mutate(icans_any = ifelse(icans_highest_grade == 0, "No", "Yes"),
       icans_any2 = ifelse(icans_any == "No", 0, 1),
       icans_gradecat2 = case_when(
         icans_highest_grade == 0                      ~ "No ICANS",
         icans_highest_grade == 1                      ~ "Grade 1",
         icans_highest_grade >= 2                      ~ "Grade 2+"),
       icans_gradecat2 = factor(icans_gradecat2, levels = c("No CRS", "Grade 1", "Grade 2+")),
       icans_gradecat3 = case_when(
         icans_highest_grade == 0                      ~ "No ICANS",
         icans_highest_grade %in% c(1:2)               ~ "Grade 1 or 2",
         icans_highest_grade >= 3                      ~ "Grade 3+"),
       icans_gradecat3 = factor(icans_gradecat3, levels = c("No CRS", "Grade 1 or 2", "Grade 3+")),
       gr3_icans = case_when(
         icans_highest_grade %in% c(1:2)               ~ "Grade <3",
         icans_highest_grade %in% c(3:5)               ~ "Grade ≥3"
       )) %>%
  mutate(gr2_icans = case_when(
    icans_highest_grade %in% c(1)                      ~ "Grade <2",
    icans_highest_grade %in% c(2:5)                    ~ "Grade ≥2"
  )) %>%
  mutate(day_of_onset_icans_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = icans_day_of_onset) /
           duration(n =1, unit = "days")
  ) %>%
  mutate(early_intervention_crs = case_when(
    crs_any == "No"                                     ~ NA_character_,
    crs_early_intervention_dex_y_n == "Yes" &
      crs_early_intervention_toci_y_n == "Yes"          ~ "Dexamethasone and Tocilizumab",
    crs_early_intervention_dex_y_n == "Yes"             ~ "Dexamethasone",
    crs_early_intervention_toci_y_n == "Yes"            ~ "Tocilizumab",
    crs_early_intervention_dex_y_n == "No" &
      crs_early_intervention_toci_y_n == "No"           ~ "No",
    TRUE                                                ~ paste(crs_early_intervention_dex_y_n, 
                                                                crs_early_intervention_toci_y_n)
  )) |> 
  mutate(hospitalized_for_crs_icans = case_when(
    crs_any == "No" &
    icans_any == "No"                                   ~ NA_character_,
    hospitalized_for_crs_icans == "Y"                   ~ "Yes",
    hospitalized_for_crs_icans == "Admitted"            ~"Admitted Prior to First CRS/ICANS"
  )) |> 
  mutate(hospitalized_time_for_crs_icans_days = case_when(
    hospitalized_for_crs_icans == "Yes"                 ~ total_days_of_hospitalization_for_crs_icans
  )) |> 
  # NINT----
  mutate(parkinsonian_neurotoxicity_yes_no = case_when(
    nint_y_n == "No"                                   ~ "No",
    str_detect(nint_type, "Parkinsonism")              ~ "Yes",
    !is.na(nint_type)                                  ~ "No",
    nint_y_n == "Yes"                                  ~ "Unk"
  )) |> 
  mutate(cnp_neurotoxicity_yes_no = case_when(
    nint_y_n == "No"                                   ~ "No",
    str_detect(nint_type, "CNP")                       ~ "Yes",
    !is.na(nint_type)                                  ~ "No",
    nint_y_n == "Yes"                                  ~ "Unk"
  )) |> 
  mutate(cnp_and_parkinsonian_neurotoxicity_yes_no = case_when(
    nint_y_n == "No"                                   ~ "No",
    str_detect(nint_type, "CNP") &
      str_detect(nint_type, "Parkinsonism")            ~ "Yes",
    !is.na(nint_type)                                  ~ "No",
    nint_y_n == "Yes"                                  ~ "Unk"
  )) |> 
  mutate(cnp_and_nonparkinsonian_neurotoxicity_yes_no = case_when(
    nint_y_n == "No"                                   ~ "No",
    str_detect(nint_type, "CNP") &
      str_detect(nint_type, "PRES|LMN")                ~ "Yes",
    !is.na(nint_type)                                  ~ "No",
    nint_y_n == "Yes"                                  ~ "Unk"
  )) |> 
  # mutate(parkinsonian_neurotoxicity_duration_days =
  #          interval(start = updated_dnt_parkinsononset_dt, end = updated_dnt_parkinsonlatest_dt) /
  #          duration(n =1, unit = "days")
  # ) %>%
  # mutate(day_of_onset_parkinsonian_relative_to_infusion =
  #          interval(start = date_of_carvykti_d0, end = updated_dnt_parkinsononset_dt) /
  #          duration(n =1, unit = "days")
  # ) %>%
  # mutate(cnp_duration_days =
  #          interval(start = updated_dnt_cnponset_dt, end = updated_dnt_cnplatest_dt) /
  #          duration(n =1, unit = "days")
  # ) %>%
  # mutate(day_of_onset_cnp_relative_to_infusion =
  #          interval(start = date_of_carvykti_d0, end = updated_dnt_cnponset_dt) /
  #          duration(n =1, unit = "days")
  # ) %>%

  mutate(day_of_onset_nint_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = nint_day_of_onset) /
           duration(n =1, unit = "days")
  ) %>%
  # mutate(day_of_icans_highest_grade_relative_to_infusion =
  #          interval(start = date_of_carvykti_d0, end = date_of_icans_highest_grade) /
  #          duration(n =1, unit = "days")
  # ) %>%
  mutate(clearance_ferritin = case_when(
    ferritin_clear < 650                               ~ "< 650",
    ferritin_clear %in% c(650:2000)                    ~ "650 - 2000",
    ferritin_clear > 2000                              ~ "> 2000"
  )) %>%
  mutate(any_infection = infectious_complications_90_day) %>%
  mutate(any_sevinfection = case_when(
    !is.na(severe_infection)                           ~ severe_infection,
    any_infection == "No"                              ~ "No"
  )) %>%
  mutate(severe_infection = case_when(
    severe_infection == "Yes"                          ~ "Severe infection",
    severe_infection == "No"                           ~ "Mild-to-Moderate infection"
  )) %>%
  mutate(severity_infection = case_when(
    !is.na(severe_infection)                           ~ severe_infection,
    any_infection == "Yes"                             ~ NA_character_,
    any_infection == "No"                              ~ "No infection"
  ), severity_infection = relevel(factor(severity_infection), ref = "No infection")) %>%
  mutate(time_from_infusion_to_infection_days =
           interval(start = date_of_carvykti_d0, end = date_of_severe_infection) /
           duration(n =1, unit = "days")
  )
```



```{r survival and response}
cart3 <- cart2 %>%
  # os
  # mutate(updated_mortality = case_when(
  #   updated_mortality == "Y"                        ~ "Yes",
  #   updated_mortality == "N"                        ~ "No"
  # )) %>%
  mutate(mortality = case_when(
    mortality == "Yes"                              ~ "Dead",
    mortality == "No"                               ~ "Alive"
  )) %>%
  # Fix event accordingly
  mutate(os_event = case_when(
    !is.na(date_of_mortality)                       ~ 1,
    is.na(date_of_mortality)                        ~ 0
  )) %>%
  mutate(os_date = coalesce(date_of_mortality, #updated_vitalstatus_dt, 
                            date_of_last_visit_contact)) %>%
  mutate(os_time_from_infusion_months =
           interval(
             start = date_of_carvykti_d0,
             end = os_date)/
           duration(n = 1, units = "months")) %>%
  mutate(updated_day_of_death_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = date_of_mortality#updated_mortality_dt
                    ) /
           duration(n = 1, unit = "days")
  ) %>%
  mutate(pfs_event = case_when(
    !is.na(date_of_progression)                     ~ 1,
    os_event == 1                                   ~ 1,
    !is.na(date_of_last_visit_contact)              ~ 0
  )) %>%
  mutate(pfs_date = case_when(
    !is.na(date_of_progression)                     ~ date_of_progression,
    os_event == 1                                   ~ os_date,
    !is.na(date_of_last_visit_contact)              ~ os_date
  )) %>%
  mutate(pfs_time_from_infusion_months =
           interval(
             start = date_of_carvykti_d0,
             end = pfs_date)/
           duration(n = 1, units = "months")) %>%
  mutate(updated_day_of_prog_relative_to_infusion =
           interval(start = date_of_carvykti_d0, end = date_of_progression) /
           duration(n = 1, unit = "days")
  )

cart3 <- cart3 %>%
  mutate(response_d30 = case_when(
    (os_event == 1 | pfs_event == 1) &
      pfs_time_from_infusion_months < 1                     ~ "Died or progressed before day 30",
    str_detect(d_30, "VGPR")      ~ "VGPR",
    str_detect(d_30, "PR")        ~ "PR",
    str_detect(d_30, "uCR")	     ~ "sCR/CR",
    str_detect(d_30, "CR")        ~ "sCR/CR",
    d_30 == "MR"                  ~ "SD",
    str_detect(d_30, "SD")        ~ "SD",
    str_detect(d_30, "PD")        ~ "PD",
    is.na(d_30)                   ~ NA_character_,
    TRUE                                               ~ d_30
  )) %>%
  mutate(response_d30_v2 = case_when(
    str_detect(response_d30, "Died")                   ~ "PD",
    is.na(response_d30)                                ~ NA_character_,
    TRUE                                               ~ response_d30
  )) %>%
  mutate(ORR_30days = case_when(
    str_detect(response_d30_v2, "CR|PR")               ~ "≥PR",
    is.na(response_d30_v2)                             ~ NA_character_,
    TRUE                                               ~ "PD/SD" # = "PD/SD/MR"
  )) %>%
  # mutate(VGPRorbetter_30days = case_when(
  #   str_detect(response_d30, "CR|VGPR")                       ~ "VGPR/CR/sCR",
  #   is.na(response_d30)                                       ~ NA_character_,
  #   TRUE                                                      ~ "PD/SD"
  # )) %>%
  mutate(CRorbetter_30days = case_when(
    str_detect(response_d30_v2, "CR")	                 ~ "sCR/CR",
    is.na(response_d30_v2)                             ~ NA_character_,
    TRUE                                               ~ "≤CR"
  )) %>%
  # mutate(CRorbetter_30days = case_when(
  #   response_d30 == "PD"	                                    ~ "Yes, PD",
  #   is.na(response_d30)                                       ~ NA_character_,
  #   TRUE                                                      ~ "No"
  # )) %>%

  mutate(response_d90 = case_when(
    (os_event == 1 | pfs_event == 1) &
      pfs_time_from_infusion_months < 3                     ~ "Died or progressed before day 90",
    str_detect(d_90, "VGPR")      ~ "VGPR",
    str_detect(d_90, "PR")        ~ "PR",
    str_detect(d_90, "uCR")	     ~ "sCR/CR",
    str_detect(d_90, "CR")        ~ "sCR/CR",
    str_detect(d_90, "Cr")        ~ "sCR/CR",
    d_90 == "MR"                  ~ "SD",
    str_detect(d_90, "SD")        ~ "SD",
    str_detect(d_90, "PD")        ~ "PD",
    is.na(d_90)                   ~ NA_character_,
    TRUE                                               ~ d_90
  )) %>%
    mutate(response_d90_v2 = case_when(
    str_detect(response_d90, "Died")                   ~ "PD",
    is.na(response_d90)                                ~ NA_character_,
    TRUE                                               ~ response_d90
  )) %>%
  mutate(ORR_90days = case_when(
    str_detect(response_d90_v2, "CR|PR")               ~ "≥PR",
    is.na(response_d90_v2)                             ~ NA_character_,
    TRUE                                               ~ "PD/SD"
  )) %>%
  mutate(CRorbetter_90days = case_when(
    str_detect(response_d90_v2, "CR")	                 ~ "sCR/CR",
    is.na(response_d90_v2)                             ~ NA_character_,
    TRUE                                               ~ "≤CR"
  )) %>%
  mutate(best_response_in90days = case_when(
    response_d30_v2 == "sCR/CR" |
      response_d90_v2 == "sCR/CR"                      ~ "sCR/CR",
    response_d30_v2 == "VGPR" |
      response_d90_v2 == "VGPR"                        ~ "VGPR",
    response_d30_v2 == "PR" |
      response_d90_v2 == "PR"                          ~ "PR",
    response_d30_v2 == "SD" |
      response_d90_v2 == "SD"                          ~ "SD",
    response_d30_v2 == "PD" |
      response_d90_v2 == "PD"                          ~ "PD",
    TRUE                                               ~ NA_character_
  )) %>%
  mutate(response_d180 = case_when(
    str_detect(d_180, "VGPR")     ~ "VGPR",
    str_detect(d_180, "PR")       ~ "PR",
    str_detect(d_180, "uCR")	     ~ "sCR/CR",
    str_detect(d_180, "CR")       ~ "sCR/CR",
    d_180 == "MR"                 ~ "SD",
    str_detect(d_180, "SD")       ~ "SD",
    str_detect(d_180, "PD")       ~ "PD",
    (os_event == 1 | pfs_event == 1) &
      pfs_time_from_infusion_months < 6                     ~ "Died or progressed before day 180",
    is.na(d_180)                  ~ NA_character_,
    TRUE                                               ~ d_180
  )) %>%
    mutate(response_d180_v2 = case_when(
    str_detect(response_d180, "Died")                  ~ "PD",
    is.na(response_d180)                               ~ NA_character_,
    TRUE                                               ~ response_d180
  )) %>%
  mutate(ORR_180days = case_when(
    str_detect(response_d180_v2, "CR|PR")              ~ "≥PR",
    is.na(response_d180_v2)                            ~ NA_character_,
    TRUE                                               ~ "PD/SD"
  )) %>%
  mutate(CRorbetter_180days = case_when(
    str_detect(response_d180_v2, "CR")	               ~ "sCR/CR",
    is.na(response_d180_v2)                            ~ NA_character_,
    TRUE                                               ~ "≤CR"
  )) %>%
  mutate(response_d360 = case_when(
    str_detect(d_365, "VGPR")     ~ "VGPR",
    str_detect(d_365, "PR")       ~ "PR",
    str_detect(d_365, "uCR")	     ~ "sCR/CR",
    str_detect(d_365, "CR")       ~ "sCR/CR",
    d_365 == "MR"                 ~ "SD",
    str_detect(d_365, "SD")       ~ "SD",
    str_detect(d_365, "PD")       ~ "PD",
    (os_event == 1 | pfs_event == 1) &
      pfs_time_from_infusion_months < 12                    ~ "Died or progressed before day 360",
    is.na(d_365)                  ~ NA_character_,
    TRUE                                               ~ d_365
  )) %>%
    mutate(response_d360_v2 = case_when(
    str_detect(response_d360, "Died")                  ~ "PD",
    is.na(response_d360)                               ~ NA_character_,
    TRUE                                               ~ response_d360
  )) %>%
  mutate(ORR_360days = case_when(
    str_detect(response_d360_v2, "CR|PR")              ~ "≥PR",
    is.na(response_d360_v2)                            ~ NA_character_,
    TRUE                                               ~ "PD/SD"
  )) %>%
  mutate(CRorbetter_360days = case_when(
    str_detect(response_d360_v2, "CR")	               ~ "sCR/CR",
    is.na(response_d360_v2)                            ~ NA_character_,
    TRUE                                               ~ "≤CR"
  )) %>%
  mutate(best_response = case_when(
    response_d30_v2 == "sCR/CR" |
      response_d90_v2 == "sCR/CR" |
      response_d180_v2 == "sCR/CR" |
      response_d360_v2 == "sCR/CR"                     ~ "sCR/CR",
    response_d30_v2 == "VGPR" |
      response_d90_v2 == "VGPR" |
      response_d180_v2 == "VGPR" |
      response_d360_v2 == "VGPR"                       ~ "VGPR",
    response_d30_v2 == "PR" |
      response_d90_v2 == "PR" |
      response_d180_v2 == "PR" |
      response_d360_v2 == "PR"                         ~ "PR",
    response_d30_v2 == "SD" |
      response_d90_v2 == "SD" |
      response_d180_v2 == "SD" |
      response_d360_v2 == "SD"                         ~ "SD",
    response_d30_v2 == "PD" |
      response_d90_v2 == "PD" |
      response_d180_v2 == "PD" |
      response_d360_v2 == "PD"                         ~ "PD",
    TRUE                                               ~ NA_character_
  )) %>%
  mutate(best_ORR = case_when(
    str_detect(best_response, "CR|PR")                 ~ "≥PR",
    str_detect(best_response, "SD|PD")                 ~ "PD/SD",
    TRUE                                               ~ NA_character_
  )) %>%
  mutate(best_CRorbetter = case_when(
     CRorbetter_30days == "sCR/CR" |
       CRorbetter_90days == "sCR/CR" |
       CRorbetter_180days == "sCR/CR" |
       CRorbetter_360days == "sCR/CR"                  ~ "sCR/CR",
     is.na(CRorbetter_30days) &
       is.na(CRorbetter_90days) &
       is.na(CRorbetter_180days) &
       is.na(CRorbetter_360days)                       ~ NA_character_,
     TRUE                                              ~ "< CR"
   )) |> 
  mutate(nrm_response = case_when(
    os_event == 0                                      ~ 0,
    # None here but keep in case
    os_event == 1 &
      cause_of_mortality %in% 
      c("Myeloma", "Myeloma Progression")              ~ 0,
    os_event == 1 &
      !is.na(date_of_progression)                      ~ 0,
    
    os_event == 1                                      ~ 1
  )) |> 
  mutate(nrm_response_d90 = case_when(
    os_event == 0                                      ~ 0,
    # None here but keep in case
    os_event == 1 &
      cause_of_mortality %in% 
      c("Myeloma", "Myeloma Progression") &
      os_time_from_infusion_months < 3                 ~ 0,
    os_event == 1 &
      !is.na(date_of_progression) &
      os_time_from_infusion_months < 3                 ~ 0,
    
    os_event == 1 &
      os_time_from_infusion_months < 3                 ~ 1,
    os_event == 1 &
      os_time_from_infusion_months > 3                 ~ 0,
    !is.na(os_event)                                   ~ 99
  ))

```

```{r exploratory function2}
# data <- cart3 %>%
#   select_if(~!is.numeric(.)) %>%
#   select_if(~!is.POSIXct(.))

# check_data <- function(data){
#
#   for(i in 1:length(colnames(data))) {
#
#     # if(class(data[[i]]) == "factor" | class(data[[i]]) == "character") {
#
#       # print(data[i])
#       print(colnames(data[i]))
#       print(str(data[[i]]))
#       print(table(data[[i]]))
#     # }
#
#   }
# }
#
# check_data(data)
```


```{r Labeling}
## Labeling ----
var_label(cart3) <- list(age_d0 = "Patient age", agecat = "Patient age - Categories",
                         male_sex = "Male Sex", sex_m_f = "Sex",
                         race = "Race", race_all = "Race (raw)",
                         # raceeth = "Race and ethnicity",
                         infused = "Infused?",
                         os_time_from_infusion_months = "Follow-up time from infusion (months)",

                         mortality = "Death",
                         # updated_mortality = "Death",
                         # day_of_death_relative_to_infusion = "Time-to-death (days)",
                         updated_day_of_death_relative_to_infusion = "Time-to-death (days)",
                         # day_of_prog_relative_to_infusion = "Time-to-progression (days)",
                         updated_day_of_prog_relative_to_infusion = "Time-to-progression (days)",


                         time_since_diagnosis_to_d0_years = "Time since diagnosis at D0 (years)",
                         extramedullary_disease_y_n = "Extramedullary disease",
                         # updated_bximag_imaging_emd_yn_preinf = "Extramedullary disease",
                         # circulating_plasma_cell = "UPDATED Circulating Plasma Cells",
                         # high_marrow_burden_50_percent = "High marrow burden (≥50%)",
                         ecog_performance_status = "ECOG",
                         ecog_cat = "ECOG (cat)" ,
                         r_iss_staging_2 = "R-ISS",
                         # updated_r_iss = "R-ISS (Gabe)",
                         cytogenetic_risk = "High risk cytogenetics",
                         # cytogenetics_incl_1q = "High risk cytogenetics (including gain 1q)",
                         # deletion_17p_prior_to_car_t_infusion_y_n = "Deletion 17p at Infusion",
                         # t_4_14_prior_to_car_t_infusion_y_n = "t(4:14) at Infusion",
                         # t_14_16_prior_to_car_t_infusion_y_n = "t(4:16) at Infusion",
                         # gain_amp1q21 = "Gain/amp 1q21",
                         number_of_prior_therapies = "Number of prior therapy",
                         number_prior_lines_therapy_cat13 = "Number of prior lines of therapy (cat)",
                         number_prior_lines_therapy_cat12 = "Number of prior lines of therapy (cat)",
                         bm_bx_pre_bridging_50_percent_plasma_cells = "BMBx Pre Bridging ≥50% plasma cells",
                         prior_transplant =	"Previous stem-cell transplantation",
                         scope_mm = "SCOPE-MM",
                         bridging_therapy_y_n = "Bridging therapy",
                         bridging_type = "Bridging therapy used",
                         bridging_response_cat_vgpr = "Bridging response",
                         bridging_response_cat_pr = "Bridging response",
                         bridging_response_cat2pr = "Bridging response (No bridging including)",
                         bridging_response_cat2vgpr = "Bridging response (No bridging including)",
                         prior_auto_sct_y_n = "Prior autoSCT",
                         prior_allo_sct_y_n = "Prior alloSCT",
                         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_y_n = "Prior BCMA-directed therapy",
                         past_exposure_to_bcma_y_n = "Prior BCMA-directed therapy",
                         # need_for_g_csf_post_infus_yes_1_no_0 = "Granulocyte colony stimulating factor (G-CSF)",
                         ivig_given_y_n = "Intravenous immunoglobulin (IVIG) prior to D0",
                         ivig_ppx = "Prophylactic IVIG given D+1 through D+90",
                         alc_aph_k_m_l = "Baseline ALC at apheresis (k/ul)", 
                         cd4_cells_aph = "Baseline CD4 at apheresis", 
                         cd8_cells_aph = "Baseline CD8 at apheresis", 
                         cd19_cells_aph = "Baseline CD19 at apheresis", 
                         nk_cells_aph = "Baseline NK at apheresis", 
                         
                         anc_d_90 = "ANC day90", 
                         plt_d_90 = "PLT day90", 
                         hgb_d_90 = "Hgb day90", 
                         alc_d_90 = "ALC day90", 
                         cd4_cells_d_90 = "CD4 cells day90", 
                         cd8_cells_d_90 = "CD8 cells day90", 
                         cd19_cells_d_90 = "CD19 cells day90", 
                         nk_cells_d_90 = "NK cells day90", 
                         # cd34_stem_cell_boost_yes_1_no_0 = "CD34 stem cell boost",
                         # day_of_neutrophil_recovery = "Day of neutrophil recovery",
                         # transfusion_postCART = "Transfusion post-CAR T",
                         # tpo_agonist_post_cart_yes_1_no_0 = "Thrombopoietin (TPO) agonist",
                         # bmicat = "BMI at apheresis - Normal, Overweight, Obese",
                         # steroid_use_y_n = "Steroid Use",
                         ppx_dex_cohort_y_n = "Received prophylactic dexamethasone",
                         crs_toci_given = "Tocilizumab Use (CRS)",
                         crs_anakinra_given = "Anakinra Use (CRS)",
                         crs_emapalumab_given = "Emapalumab Use (CRS)",
                         crs_tx_dex_y_n = "Dexamethasone Use (CRS)",
                         icans_anakinra_given = "Anakinra Use (ICANS)",
                         icans_tx_dex_y_n = "Dexamethasone Use (ICANS)",
                         # crs_or_icans_dex_given_y_n = "Dexamethasone Use (CRS or ICANS)",
                         # crs_and_icans_dex_given_y_n = "Dexamethasone Use (CRS and ICANS)",
                         total_cumulative_dose_d_1_d_30_days = "Cumulative steroids received during first 30 days",
                         proteasome = "Refractory to Proteasome Inhibitors",
                         lenalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Lenalidomide",
                         bortezomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Bortezomib",
                         carfilzomib_exposed_vs_refractory_vs_not_exposed = "Refractory to Carfilzomib",
                         pomalidomide_exposed_vs_refractory_vs_not_exposed = "Refractory to Pomalidomide",
                         dara = "Refractory to Daratumumab or Isatuximab",
                         immuno = "Refractory to Immunomodulators", doubleref = "Double refractory",
                         tripleref= "Triple refractory",
                         pentaref= "Penta refractory",
                         # bmicat2 = "BMI at apheresis - Normal vs. Overweight/Obese",
                         hospital_admit_y_n = "Required hospitalization",
                         hospitalized_for_crs_icans = "Required hospitalization for CRS/ICANS",
                         hospitalized_time_for_crs_icans_days = "Total Number of Days Admitted for CRS/ICANS",
                         peak_alc = "Peak ALC",
                         # peak_alc_grouping = "Peak ALC between days 8 and 19 - from column CC - seems wrong",
                         peak_alc_grouping_recoded = "Peak ALC ≥3.0 (recoded)",
                         alc_treated = "Lymphocytosis treated for peak ALC ≥3.0",
                         crs_any = "Any CRS", crs_highest_grade = "Max CRS grade (0-5)",
                         crs_gradecat2 = "CRS Grade 2+ (including no CRS)",
                         crs_gradecat3 = "CRS Grade 3+ (including no CRS)",
                         gr2_crs = "CRS Grade 2+", gr3_crs = "CRS Grade 3+",
                         day_of_onset_crs_relative_to_infusion = "Day of onset of CRS relative to infusion",
                         # day_of_max_crs_relative_to_infusion = "Day of Max CRS (relative to infusion)",
                         crs_duration_days = "Duration of CRS (days)",
                         early_intervention_crs = "Early Intervention for CRS",

                         icans_any = "Any ICANS", icans_highest_grade = "Max ICANS grade (0-5)",
                         icans_gradecat2 = "ICANS Grade 2+ (including no ICANS)",
                         icans_gradecat3 = "ICANS Grade 3+ (including no ICANS)",
                         gr2_icans = "ICANS Grade 2+", gr3_icans = "ICANS Grade 3+",

                         day_of_onset_icans_relative_to_infusion = "Day of onset of ICANS relative to infusion",
                         # day_of_icans_highest_grade_relative_to_infusion = "Day of Max ICANS (relative to infusion)",
                         icans_duration_days = "Duration of ICANS (days)",
                         nint_y_n = "NINT (Parkinsonian + CNP)",
                         nint_type = "NINT type",
                         parkinsonian_neurotoxicity_yes_no = "Parkinsonian Neurotoxicity",
                         cnp_neurotoxicity_yes_no = "CNP Neurotoxicity",
                         cnp_and_parkinsonian_neurotoxicity_yes_no = "CNP + Parkinsonian Neurotoxicity",
                         cnp_and_nonparkinsonian_neurotoxicity_yes_no = "CNP + Non Parkinsonian Neurotoxicity",
                         # updated_dnt_parkinson_yn = "Parkinsonian NT",
                         # parkinsonian_neurotoxicity_duration_days = "Parkinsonian NT duration (days)",
                         # updated_dnt_parkinsonresolved_yn = "Parkinsonian NT resolved",
                         # day_of_onset_parkinsonian_relative_to_infusion = "Day of onset of Parkinsonian NT relative to infusion",
                         # updated_dnt_cnp_yn = "CNP Neurotoxicity",
                         # updated_dnt_cnpresolved_yn = "CNP Neurotoxicity resolved",
                         # cnp_duration_days = "CNP Neurotoxicity duration (days)",
                         # day_of_onset_cnp_relative_to_infusion = "Day of onset of CNP relative to infusion",

                         day_of_onset_nint_relative_to_infusion = "Day of onset of NINT relative to infusion",

                         nint_ivig_given = "IVIG Use (NINT)",
                         nint_tx_dex_y_n = "Dexamethasone Use (overall NINT) - column DS",
                         any_infection = "Any infection",
                         any_sevinfection = "Any severe infection",
                         severe_infection = "Infection severity",
                         severity_infection = "Infection",
                         # parkinsonian_neurotoxicity_y_n = "Parkinsonian Neurotoxicity",
                         # other_delayed_non_parkinsonian_neurologic_toxicity_y_n =
                         #   "Other/Delayed Non-Parkinsonian Neurologic Toxicity",
                         carvykti_cell_dose = "CAR-T infusion dose",
                         # best_ORRcollapsed = "Best ORR at ≤ 12 months",
                         d_30 = "Response at day 30",
                         response_d30 = "Response at day 30",
                         response_d30_v2 = "Day 30 Response - Death as PD",
                         ORR_30days = "Day 30 ORR", CRorbetter_30days = "Day 30 CR or better",

                         d_90 = "Response at day 90",
                         response_d90 = "Response at day 90",
                         response_d90_v2 = "Day 90 Response - Death as PD",
                         ORR_90days = "Day 90 ORR", CRorbetter_90days = "Day 90 CR or better",

                         nrm_response = "NRM",
                         d_30_non_relapse_mortality = "30-day non-relapse mortality",
                         nrm_response_d90 = "90-day non-relapse mortality",
                         car_hematotox_score_aph = "CAR-HEMATOTOX score at apheresis",
                         car_hematotox_score_aph_cat = "CAR-HEMATOTOX score at apheresis (cat)",
                         car_hematotox_score_clear = "CAR-HEMATOTOX score at clearance",
                         car_hematotox_score_clear_cat3plus = "CAR-HEMATOTOX score at clearance (cat)",
                         car_hematotox_score_clear_cat4plus = "CAR-HEMATOTOX score at clearance (cat)",

                         best_response_in90days = "Best response in first 90 days",
                         best_response = "Best overall response",
                         best_ORR = "Best overall ORR",
                         best_CRorbetter = "Best overall CR or better"
)

```
<br>


# Tables

```{r infused}
# cart3 %>%
#   select(`infused?` = infused) %>%
#   tbl_summary(missing = "no") %>%
#   bold_labels() %>% add_stat_label()
# cart3 %>% select(mrn,carvykti_cell_dose,
#                  carvykti_cell_dose) %>% filter(is.na(carvykti_cell_dose))
```

## Table 1. Patient baseline characteristics
```{r Table 1}
cart3 %>%
  select(age_d0,
         time_since_diagnosis_to_d0_years,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone - IQR**")

cart3 %>%
  select(os_time_from_infusion_months,,
         age_d0, agecat, #male_sex,
         sex_m_f, race, race_all,
         ecog_performance_status, ecog_cat,
         
         time_since_diagnosis_to_d0_years,
         extramedullary_disease_y_n, # updated_bximag_imaging_emd_yn_preinf,
         cytogenetic_risk,
         r_iss_staging_2,
         # updated_r_iss,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         number_of_prior_therapies,
         number_prior_lines_therapy_cat12, number_prior_lines_therapy_cat13,
         prior_transplant, #prior_auto_sct_y_n, prior_allo_sct_y_n,
         bm_bx_pre_bridging_50_percent_plasma_cells,
         scope_mm,
         bridging_therapy_y_n,
         bridging_type,
         bridging_response_cat_vgpr, 
         bridging_response_cat_pr,
         bridging_response_cat2pr,
         bridging_response_cat2vgpr,
         past_exposure_to_bcma_y_n,
         # car_hematotox_score_aph, car_hematotox_score_aph_cat,
         car_hematotox_score_clear, 
         car_hematotox_score_clear_cat3plus, car_hematotox_score_clear_cat4plus,
         ivig_given_y_n,
         ivig_ppx,
         carvykti_cell_dose,
         # updated_cartchar_infusion_dose,
         alc_aph_k_m_l, cd4_cells_aph, cd8_cells_aph,
         cd19_cells_aph, nk_cells_aph,
         anc_d_90, plt_d_90,
         hgb_d_90, alc_d_90,
         cd4_cells_d_90, cd8_cells_d_90,
         cd19_cells_d_90, nk_cells_d_90,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              type = list(
                c(#car_hematotox_score_aph,
                  all_dichotomous())
                ~"categorical",
                c(number_of_prior_therapies,
                  carvykti_cell_dose) ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              digits = all_continuous() ~ 1
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**")
```
One patient has a missing cell dose in Gabe's data which recorded = 6e+05 in the prophyl data. Gabe verified it and I fixed it (0.6).

<br>

## Table 2. Safety
### CRS/ICANS
```{r}
# breaka #for IQR??
cart3 %>%
  select(peak_alc,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone - IQR**")


cart3 %>%
  select(hospitalized_for_crs_icans,
         hospitalized_time_for_crs_icans_days,
         #hospital_admit_y_n,
         peak_alc, peak_alc_grouping_recoded,
         # peak_alc_grouping,
         alc_treated,
         any_infection, any_sevinfection,
         severity_infection, # severe_infection,
         
         crs_highest_grade, crs_any, #crs_y_n,
         crs_gradecat2, crs_gradecat3,
         gr2_crs, gr3_crs,
         day_of_onset_crs_relative_to_infusion, #crs_d,
         # day_of_max_crs_relative_to_infusion,
         crs_duration_days,
         crs_toci_given, #crs_number_of_toci_doses,
         crs_tx_dex_y_n,
         crs_anakinra_given,
         crs_emapalumab_given,
         # crs_days_of_tx_dex, crs_tx_dex_given,
         # crs_days_of_anakinra, crs_other_therapies,
         early_intervention_crs,

         icans_highest_grade, icans_any, #icans_y_n,
         icans_gradecat2, icans_gradecat3,
         gr2_icans, gr3_icans,
         day_of_onset_icans_relative_to_infusion, #icans_d,
         # day_of_icans_highest_grade_relative_to_infusion,
         icans_duration_days,
         icans_tx_dex_y_n,
         icans_anakinra_given,
         # icans_days_of_tx_dex, icans_tx_dex_given,
         #icans_days_of_anakinra, icans_other_therapies,
         # crs_or_icans_dex_given_y_n,
         # crs_and_icans_dex_given_y_n,
         # crs_icans_days_of_tx_dex, crs_icans_dex_given,
         total_cumulative_dose_d_1_d_30_days,
         ppx_dex_cohort_y_n
         ) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              type = list(c(all_dichotomous()) ~ "categorical",
                          c(hospitalized_time_for_crs_icans_days,
                            crs_duration_days, day_of_onset_icans_relative_to_infusion,
                            icans_duration_days) ~ "continuous")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**")
```
For "Emapalumab Use (CRS)", I am assuming the use of Emapalumab is for CRS as the name of the variable is "CRS Other Therapies".
I coded "No" for all the patients with CRS any grade that didn't receive Emapalumab.

<br>

### NINT
```{r}
cart3 %>%
  select(nint_type) |> 
  tbl_summary()
         
cart3 %>%
  select(parkinsonian_neurotoxicity_yes_no, 
         cnp_neurotoxicity_yes_no, 
         cnp_and_parkinsonian_neurotoxicity_yes_no, 
         cnp_and_nonparkinsonian_neurotoxicity_yes_no,
         # updated_dnt_parkinsonresolved_yn,
         # day_of_onset_parkinsonian_relative_to_infusion,
         # updated_dnt_cnp_yn,
         # updated_dnt_cnpresolved_yn,
         # day_of_onset_cnp_relative_to_infusion,


         nint_y_n, #nint_type,
         day_of_onset_nint_relative_to_infusion, #nint_d,
         # parkinsonian_neurotoxicity_yes_no,

         # nint_tx_dex_y_n, #nint_days_of_tx_dex, nint_tx_dex_given,
         # nint_ivig_given, #nint_other_therapies,
         ppx_dex_cohort_y_n
         ) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              type = list(c(all_dichotomous()) ~ "categorical",
                          c(day_of_onset_nint_relative_to_infusion) ~ "continuous"
                          )#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**")
```


## In response to comment regarding CRS incidence and severity between both cohorts subgrouped based on clearance ferritin (<650 vs 650-2000 vs >2000)
```{r}
cart3 %>%
  filter(clearance_ferritin == "< 650") %>%
  mutate(ppx_dex_cohort_y_n = case_when(
    ppx_dex_cohort_y_n == "Yes"        ~ "Recieved prophy dex",
    ppx_dex_cohort_y_n == "No"         ~ "Did not recieved prophy dex"
  )) %>%
  select(crs_highest_grade, crs_any,
         crs_gradecat2, crs_gradecat3,
         gr2_crs, gr3_crs,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              type = list(c(all_dichotomous()) ~ "categorical")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_header(label ~ "**Cohort =<br> Clearance ferritin group <650**") %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Clearance ferritin group <650**")

cart3 %>%
  filter(clearance_ferritin == "650 - 2000") %>%
  mutate(ppx_dex_cohort_y_n = case_when(
    ppx_dex_cohort_y_n == "Yes"        ~ "Recieved prophy dex",
    ppx_dex_cohort_y_n == "No"         ~ "Did not recieved prophy dex"
  )) %>%
  select(crs_highest_grade, crs_any,
         crs_gradecat2, crs_gradecat3,
         gr2_crs, gr3_crs,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              type = list(c(all_dichotomous()) ~ "categorical")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_header(label ~ "**Cohort =<br> Clearance ferritin group 650 - 2000**") %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Clearance ferritin group 650 - 2000**")

cart3 %>%
  filter(clearance_ferritin == "> 2000") %>%
  mutate(ppx_dex_cohort_y_n = case_when(
    ppx_dex_cohort_y_n == "Yes"        ~ "Recieved prophy dex",
    ppx_dex_cohort_y_n == "No"         ~ "Did not recieved prophy dex"
  )) %>%
  select(crs_highest_grade, crs_any,
         crs_gradecat2, crs_gradecat3,
         gr2_crs, gr3_crs,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              digits = all_continuous() ~ 1,
              type = list(c(all_dichotomous()) ~ "categorical")#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_header(label ~ "**Cohort =<br> Clearance ferritin group > 2000**") %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Clearance ferritin group > 2000**")
```
<br>

## Table 3. Efficacy/response
```{r table 2 outcome}
cart3 %>%
  select(# d_30,
         # response_d30,
         response_d30_v2,
         ORR_30days, CRorbetter_30days,
         # d_90,
         # response_d90,
         response_d90_v2,
         ORR_90days, CRorbetter_90days,
         best_response_in90days,
         best_response,
         best_ORR, best_CRorbetter,
         # updated_day_of_prog_relative_to_infusion,
         # nrm_response,
         # nrm_response_d90,
         # mortality,
         # updated_day_of_death_relative_to_infusion,
         ppx_dex_cohort_y_n) %>%
  tbl_summary(by = ppx_dex_cohort_y_n,
              type = list(
                c(all_dichotomous())
                ~ "categorical"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"),
              digits = all_continuous() ~ 1#,
              # missing = "no"
  ) %>%
  bold_labels() %>%
  add_p() %>% bold_p() %>% add_overall() %>%
  add_stat_label() %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Received prophylactic dexamethasone**")
```


```{r}
cart3 %>%
  filter(mortality == "Dead") %>%
  select(`Cause of death` = cause_of_mortality) %>%
  tbl_summary() %>%
  bold_labels() %>%
  add_stat_label()

# cart3 %>%
#   filter(!is.na(updated_outcomes_prog_dt)) %>%
#   select(mrn,updated_outcomes_prog_dt, updated_day_of_prog_relative_to_infusion,
#          starts_with("updated_outcomes_resp_")) %>%
#   arrange(updated_day_of_prog_relative_to_infusion)
```



```{r death check}

# death_dat <- cart3 %>%
#   # filter(updated_mortality == "Y") %>%
#   # filter((!is.na(date_of_mortality))) %>%
#   select(mrn, mortality,
#          date_of_mortality,
#          # day_of_death_relative_to_infusion,
#          # d_30,
#          updated_mortality,
#          # updated_day_of_death_relative_to_infusion,
#          updated_mortality_dt, , date_of_last_visit_contact, updated_vitalstatus_dt)
#
# cart3 %>%
#   filter(mortality == "Yes") %>%
#   filter((!is.na(date_of_mortality))) %>%
#   select(mrn, mortality,
#          # day_of_death_relative_to_infusion,
#          d_30,
#          updated_mortality,
#          # updated_day_of_death_relative_to_infusion,
#          updated_mortality_dt, date_of_mortality, date_of_last_visit_contact)
```

# Survival
## OS
```{r KM OS}
ggsurvplot(survfit(Surv(os_time_from_infusion_months, os_event) ~ 1,
                   data=cart3),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(os_time_from_infusion_months, os_event) ~ ppx_dex_cohort_y_n,
                   data=cart3),
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

Median OS in months
```{r}
survfit(Surv(time = cart3$os_time_from_infusion_months,
                   event = cart3$os_event) ~ 1,
              data = cart3) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  ) %>% add_nevent() %>% add_n()
survfit(Surv(time = cart3$os_time_from_infusion_months,
                   event = cart3$os_event) ~ ppx_dex_cohort_y_n,
              data = cart3) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median survival (95% CI)**"
  ) %>% add_nevent() %>% add_n()

list(
  survfit(Surv(time = cart3$os_time_from_infusion_months,
               event = cart3$os_event) ~ 1,
          data = cart3),
  survfit(Surv(time = cart3$os_time_from_infusion_months,
               event = cart3$os_event) ~ ppx_dex_cohort_y_n,
          data = cart3)
) %>%
  tbl_survfit(times = c(6, 12),
              label_header = "**OS Rate at {time} Months**")

```

## PFS
```{r KM PFS}
ggsurvplot(survfit(Surv(pfs_time_from_infusion_months, pfs_event) ~ 1,
                   data=cart3),
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(pfs_time_from_infusion_months, pfs_event) ~ ppx_dex_cohort_y_n,
                   data=cart3),
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

Median PFS in months
```{r}
survfit(Surv(time = cart3$pfs_time_from_infusion_months,
                   event = cart3$pfs_event) ~ 1,
              data = cart3) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median PFS (95% CI)**"
  ) %>% add_nevent() %>% add_n()
survfit(Surv(time = cart3$pfs_time_from_infusion_months,
                   event = cart3$pfs_event) ~ ppx_dex_cohort_y_n,
              data = cart3) %>%
  tbl_survfit(
    probs = 0.5,
    label_header = "**Median PFS (95% CI)**"
  ) %>% add_nevent() %>% add_n()

list(
  survfit(Surv(time = cart3$pfs_time_from_infusion_months,
               event = cart3$pfs_event) ~ 1,
          data = cart3),
  survfit(Surv(time = cart3$pfs_time_from_infusion_months,
               event = cart3$pfs_event) ~ ppx_dex_cohort_y_n,
          data = cart3)
) %>%
  tbl_survfit(times = c(6, 12),
              label_header = "**PFS Rate at {time} Months**")

```

# NRM
```{r}
ggsurvplot(survfit(Surv(os_time_from_infusion_months, nrm_response) ~ ppx_dex_cohort_y_n,
                   data=cart3),
           fun = "event",
           font.main = c(20, "bold", "black"),
           font.x = c(12, "plain", "black"),
           font.y = c(12, "plain", "black"),
           font.legend = c(10, "plain", "black"),
           font.tickslab = c(10, "plain", "black"),
           size = 1.5,
           surv.median.line = "hv",

           xlab = "Time (months)",
           ylab = "Cumulative Incidence of NRM",
           legend = "top", legend.title = "",
           # legend.labs = c("No", "t(11;14) alone", "t(11;14) and other risk(s)"),
           pval = TRUE, pval.size = 4,
           conf.int = FALSE,
           risk.table = TRUE,
           risk.table.fontsize = 3,
           tables.y.text = FALSE,
           tables.theme = theme_classic()+
             theme(text = element_text(size = 10),
                   # plot.title = element_text(size = 10),  # Table title ("Number at risk")
                   axis.text.x = element_text(size = 10),                # Time ticks (x-axis)
                   axis.title.x = element_text(size = 12)                # X-axis label ("Time")
             ),
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 3))
```



# MVA (bridging response as VGPR or better)
## OS
Model 1 = CAR-HEMATOTOX + BM PCs >50% + EMD + bridging response + penta-refractory status
```{r}
coxph(Surv(time = cart3$os_time_from_infusion_months,
           event = cart3$os_event) ~ ppx_dex_cohort_y_n + car_hematotox_score_aph_cat +
        bm_bx_pre_bridging_50_percent_plasma_cells + extramedullary_disease_y_n +
        bridging_response_cat_vgpr + pentaref,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 2 = Model 1 + ECOG PS ≥2.   
The model cannot be estimated because of complete separation of values for ECOG.
```{r}
# coxph(Surv(time = cart3$os_time_from_infusion_months,
#            event = cart3$os_event) ~ ppx_dex_cohort_y_n + car_hematotox_score_aph_cat +
#         bm_bx_pre_bridging_50_percent_plasma_cells + extramedullary_disease_y_n +
#         bridging_response_cat_vgpr + pentaref +
#         ecog_cat,
#       data = cart3)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
```

Model 3 = SCOPE-MM, bridging response, penta-refractory status
```{r}
coxph(Surv(time = cart3$os_time_from_infusion_months,
           event = cart3$os_event) ~ ppx_dex_cohort_y_n + scope_mm +
        bridging_response_cat_vgpr + pentaref,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 4 = Model 3 + ECOG PS ≥2
```{r}
coxph(Surv(time = cart3$os_time_from_infusion_months,
           event = cart3$os_event) ~ ppx_dex_cohort_y_n + scope_mm +
        bridging_response_cat_vgpr + pentaref +
      ecog_cat,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

## PFS
Model 1 = CAR-HEMATOTOX + BM PCs >50% + EMD + bridging response + penta-refractory status
```{r}
coxph(Surv(time = cart3$pfs_time_from_infusion_months,
           event = cart3$pfs_event) ~ ppx_dex_cohort_y_n + car_hematotox_score_aph_cat +
        bm_bx_pre_bridging_50_percent_plasma_cells + extramedullary_disease_y_n +
        bridging_response_cat_vgpr + pentaref,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 2 = Model 1 + ECOG PS ≥2
```{r}
coxph(Surv(time = cart3$pfs_time_from_infusion_months,
           event = cart3$pfs_event) ~ ppx_dex_cohort_y_n + car_hematotox_score_aph_cat +
        bm_bx_pre_bridging_50_percent_plasma_cells + extramedullary_disease_y_n +
        bridging_response_cat_vgpr + pentaref +
        ecog_cat,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 3 = SCOPE-MM, bridging response, penta-refractory status
```{r}
coxph(Surv(time = cart3$pfs_time_from_infusion_months,
           event = cart3$pfs_event) ~ ppx_dex_cohort_y_n + scope_mm +
        bridging_response_cat_vgpr + pentaref,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 4 = Model 3 + ECOG PS ≥2
```{r}
coxph(Surv(time = cart3$pfs_time_from_infusion_months,
           event = cart3$pfs_event) ~ ppx_dex_cohort_y_n + scope_mm +
        bridging_response_cat_vgpr + pentaref +
        ecog_cat,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

# MVA (bridging response as PR or better)
## OS
Model 1 = CAR-HEMATOTOX + BM PCs >50% + EMD + bridging response + penta-refractory status.
```{r}
coxph(Surv(time = cart3$os_time_from_infusion_months,
           event = cart3$os_event) ~ ppx_dex_cohort_y_n + car_hematotox_score_aph_cat +
        bm_bx_pre_bridging_50_percent_plasma_cells + extramedullary_disease_y_n +
        bridging_response_cat_pr + pentaref,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 2 = Model 1 + ECOG PS ≥2.  
The model cannot be estimated because of complete separation of values for ECOG.
```{r}
# coxph(Surv(time = cart3$os_time_from_infusion_months,
#            event = cart3$os_event) ~ ppx_dex_cohort_y_n + car_hematotox_score_aph_cat +
#         bm_bx_pre_bridging_50_percent_plasma_cells + extramedullary_disease_y_n +
#         bridging_response_cat_pr + pentaref +
#         ecog_cat,
#       data = cart3)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
```

Model 3 = SCOPE-MM, bridging response, penta-refractory status
```{r}
coxph(Surv(time = cart3$os_time_from_infusion_months,
           event = cart3$os_event) ~ ppx_dex_cohort_y_n + scope_mm +
        bridging_response_cat_pr + pentaref,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 4 = Model 3 + ECOG PS ≥2
```{r}
coxph(Surv(time = cart3$os_time_from_infusion_months,
           event = cart3$os_event) ~ ppx_dex_cohort_y_n + scope_mm +
        bridging_response_cat_pr + pentaref +
      ecog_cat,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

## PFS
Model 1 = CAR-HEMATOTOX + BM PCs >50% + EMD + bridging response + penta-refractory status
```{r}
coxph(Surv(time = cart3$pfs_time_from_infusion_months,
           event = cart3$pfs_event) ~ ppx_dex_cohort_y_n + car_hematotox_score_aph_cat +
        bm_bx_pre_bridging_50_percent_plasma_cells + extramedullary_disease_y_n +
        bridging_response_cat_pr + pentaref,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 2 = Model 1 + ECOG PS ≥2
```{r}
coxph(Surv(time = cart3$pfs_time_from_infusion_months,
           event = cart3$pfs_event) ~ ppx_dex_cohort_y_n + car_hematotox_score_aph_cat +
        bm_bx_pre_bridging_50_percent_plasma_cells + extramedullary_disease_y_n +
        bridging_response_cat_pr + pentaref +
        ecog_cat,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 3 = SCOPE-MM, bridging response, penta-refractory status
```{r}
coxph(Surv(time = cart3$pfs_time_from_infusion_months,
           event = cart3$pfs_event) ~ ppx_dex_cohort_y_n + scope_mm +
        bridging_response_cat_pr + pentaref,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

Model 4 = Model 3 + ECOG PS ≥2
```{r}
coxph(Surv(time = cart3$pfs_time_from_infusion_months,
           event = cart3$pfs_event) ~ ppx_dex_cohort_y_n + scope_mm +
        bridging_response_cat_pr + pentaref +
        ecog_cat,
      data = cart3)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```
